---
title: "Quality checks"
author: "Seabird Monitoring"
date: "Last update: 16/06/2025"
output: html_document
---

# Packages

Load the packages.

```{r, warning=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(beepr)
library(here)
```

# Data

Please tell me where is the data

```{r}
ThisDirectory<-(here::here('00Data')) 
```

Run me to show you the files in the folder

```{r}
list.files(ThisDirectory,pattern = ".xlsx")
```

Tell me which file do you want to report

```{r}
ThisFile<- "Test_20250616_AreaA.xlsx"
```

## Tripdaten

```{r}
TripDaten<-read_excel(path=paste0(ThisDirectory,'\\',ThisFile),sheet="Tripdaten",col_names = TRUE)
```

## BasisDaten

```{r}
BasisDaten<-read_excel(path=paste0(ThisDirectory,'\\',ThisFile),sheet = "Basisdaten",col_names = TRUE)
```

## Observations

```{r, warning=FALSE}
Observations<-read_excel(path=paste0(ThisDirectory,'\\',ThisFile),sheet="Observations", col_types = "text")
```

## Corrections

```{r}
Corrections<-'No manual corrections were needed'
```

# ~~~~~~~~~~~
# Formal Check

This part checks that all columns are correct and whether NA's occurred. 

## Define folder

Where is the function?

```{r input1}
FormalCheck_input_folder <- here() 
FormalCheck_input_file <- paste0(FormalCheck_input_folder,"\\01FormalCheck.Rmd") 
FormalCheck_input_file
```

Where should the output be saved?
Ideally there would be a folder 01FormalCheck to store the results.

```{r}
FormalCheck_output_folder <-paste0(FormalCheck_input_folder,"\\01FormalCheck\\") 
```

## Define names

Define the name of the file using the information provided in the Trip information. 

```{r}
FormalCheck_file_date<-as.character(TripDaten$DATE[1])
FormalCheck_file_date
FormalCheck_file_area<-as.character(TripDaten$CLUSTER[1])
FormalCheck_file_area
FormalCheck_output_name<-paste0(FormalCheck_output_folder,
                                "FormalCheck_DATE_",FormalCheck_file_date,
                                "_AREA_",FormalCheck_file_area,".html")
FormalCheck_output_name 
```

## Run 

Run to export document

```{r render validation, include=FALSE, cache=TRUE}
rmarkdown::render(
  input= FormalCheck_input_file, 
  output_format = "html_document",
  output_dir = FormalCheck_output_folder,
  params = list(
    ThisDirectory = ThisDirectory,
    ThisFile = ThisFile,
    TripDaten = TripDaten,
    BasisDaten = BasisDaten,
    Observations = Observations
  ),
  run_pandoc = TRUE,
  output_file = FormalCheck_output_name  
)
beep(sound = 1, expr = NULL)
```


# ~~~~~~~~~

# Report

## Define folder

What base to use?

```{r}
Plausability_input_folder<-here() 
Plausability_input_file<- paste0(Plausability_input_folder,"\\02PlausabilityCheck.Rmd") 
```

How do you want the output to be saved?

```{r input}
PlausabilityCheck_output_folder <- paste0(Plausability_input_folder,"\\02PlausabilityCheck\\") 
PlausabilityCheck_output_folder
```

## Define names

```{r}
unique(TripDaten$TRIP_ID)
```

If there are several TRIP_IDs, make reports separately by TRIP_ID

```{r}
Plausability_output_folder<-paste0(Plausability_input_folder,"\\02PlausabilityCheck\\") 
Plausability_file_date<-as.character(TripDaten$DATE[1])
Plausability_file_date
Plausability_file_area<-as.character(TripDaten$CLUSTER[1])
Plausability_file_area
Plausability_output_name<-paste0(Plausability_output_folder,
                                "Plausability_DATE_",Plausability_file_date,
                                "_AREA_",Plausability_file_area,".doc")
Plausability_output_name 
```

## Run

Run to export document

```{r render validation, include=FALSE}
rmarkdown::render(
  input= Plausability_input_file, 
  output_format = "word_document", #can be changed to html document
  output_dir = Plausability_output_folder,
  params = list(
    ThisDirectory = ThisDirectory,
    ThisFile = ThisFile,
    TripDaten = TripDaten,
    BasisDaten = BasisDaten,
    Observations = Observations
  ),
  run_pandoc = TRUE,
  output_file = Plausability_output_name 
)
beep(sound = 1, expr = NULL)
```

# ~~~~~~~~~~

# Maps

## Define folder
Where is the function?

```{r input}
Maps_input_folder<-here() #Where is the parametrization file
Maps_input_file <- paste0(Maps_input_folder,"\\03MapsInteractive.Rmd") 
```

## Define names
How do you want the output to be named?

```{r input}
Maps_output_folder <- paste0(Maps_input_folder,"\\03Maps\\") 
```

```{r}
Maps_output_name <- paste0(Maps_output_folder,
                           "03Maps_DATE_",
                           as.character(TripDaten$DATE[1]),
                           "_AREA_",
                           as.character(TripDaten$CLUSTER[1]),
                           ".html") 
Maps_output_name 
```

## Run

Run to export maps

```{r render validation, include=FALSE}
rmarkdown::render(
  input= Maps_input_file, 
  output_format = "html_document",
  output_dir = Maps_output_folder,
  params = list(
    ThisDirectory = ThisDirectory,
    ThisFile = ThisFile,
    BasisDaten = BasisDaten,
    Observations = Observations
  ),
  run_pandoc = TRUE,
  output_file = Maps_output_name
)
beep(sound = 1, expr = NULL)
```


**End of document**