---
title: "FormalCheck"
author: "Seabird Monitoring"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  ThisDirectory: ThisDirectory
  ThisFile: ThisFile
  TripDaten: TripDaten
  BasisDaten: BasisDaten
  Observations: Observations
  
---

# Intro

Using data from `r params$ThisFile` excel file.  

Here we will:  

-  Check **relevant** columns to see if they are all filled and valid.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=F}
library(readxl)
library(knitr)
library(ggplot2)
```

Corrections included:

```{r, echo=FALSE}
if(length(Corrections==0)==FALSE){
         print(paste0("No corrections needed"))
        }else{  
           print(paste0("Corrections were made: ",Corrections))
      }
```


```{r}
TripDaten<-TripDaten
```

# 1.Trip Data
At this part we would check that all the columns have information, and what type of information they contain. 

```{r Elements on the document, include=T, comment=NA, echo=FALSE}
cat(paste('The document contains',nrow(TripDaten),'rows, and',ncol(TripDaten),'columns.'))
cat(paste('The columns names are: '))
cat(colnames(TripDaten))
```

## Column checks

```{r, include=FALSE, echo=FALSE}
TripDatenExpectedColumns<-c("TRIP","TRIP_ID","Dataset_ID","CRUISENO","OWPAS","PROJECT","CLUSTER","LAB","SCIENTIST","DATATYPE","TECHNIQUE","OBSERVER","PLANE","NUMBER_OF_PLANES","DOUBLE_PLATFORM","DATE","STARTTIME","ENDTIME","CAMERA_SYSTEM","RESOLUTION","PLANE_FLIGHT_HEIGHT_PLANED" ,"STRIP_WIDTH","PLANE_SPEED","POSITION_ACCURACY","METHOD_ID","AREA_OBSERVED","AREA_ANALYSED","AREA_CONTROLLED", "ID_CONTROLLED","SCREENING_CONTROL_DIFFERENCE","ID_CONTROL_DIFFERENCE","QUALITY_IMPROVEMENT","POSITIONSYSTEM","POSIT_PRECISION_CODE","REFSYSTEM","NOTES")
```

```{r Check columns1, include=T, echo=F, comment=NA}
cat(paste('\n Expected',length(TripDatenExpectedColumns),'columns and',ncol(TripDaten),'provided', sep=" "))
```

```{r, echo=FALSE}
ExpectedColumns<-TripDatenExpectedColumns
ProvidedColumns<-colnames(TripDaten)
MaxColumns <- max(length(ExpectedColumns), length(ProvidedColumns))
length(ExpectedColumns) <- MaxColumns                      
length(ProvidedColumns) <- MaxColumns
ExpectedColumns<-data.frame(name=c(ExpectedColumns),expected=ExpectedColumns)
ProvidedColumns<-data.frame(name=c(ProvidedColumns),provided=ProvidedColumns)
ComparisonColumns<-merge(ExpectedColumns,ProvidedColumns,by='name',all=TRUE)
colnames(ComparisonColumns)<-c('Name','Expected','Provided')
ComparisonColumns<-ComparisonColumns %>% drop_na(Name)
```

```{r, echo=FALSE}
ComparisonTripDaten<-ComparisonColumns %>% dplyr::select(Expected,Provided)
colnames(ComparisonTripDaten)<-c("Expected","Provided")
```

Check if the name of the columns in the documents coincide, if 'TRUE' they coincide, if 'FALSE' please check.

```{r, echo=FALSE, include=FALSE}
TripDatenColumns<-colnames(TripDaten)
class(TripDatenExpectedColumns)
class(TripDatenColumns)
```

```{r, echo=FALSE}
CheckColumnNames<-function(DatenColumns=DatenColumns,DatenOriginalColumns=DatenOriginalColumns){
    DifferentTripDaten<-setdiff(TripDatenExpectedColumns,TripDatenColumns)
      if(length(DifferentTripDaten==0)==FALSE){
         print(paste0("All columns names seem to be correct or were corrected manually"))
        }else{  
           print(paste0("Please check that all columns are correct named. ",DifferentTripDaten," does not coincide with expected names."))
      }
}
```

```{r, echo=FALSE}
CheckColumnNames(DatenColumns=TripDatenColumns,DatenOriginalColumns=TripDatenExpectedColumns)
```

Values **NA** indicate if the columns were provided or are missing. 

```{r TableCol, echo=FALSE}
knitr::kable(ComparisonTripDaten)
```

Missing columns include:

```{r}
if((nrow(ComparisonTripDaten %>%
  filter(is.na(Provided)))>0)==FALSE){
         cat(("There are no missing columns"))
        }else{knitr::kable(ComparisonTripDaten %>%
  filter(is.na(Provided)))}
```

**TRIP_ID** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$TRIP_ID))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided in TRIP_ID. 

```{r}
unique(TripDaten$TRIP_ID)
```

**DATE** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$DATE))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for **DATE**.
Format expected (YYYYMMDD).
Format provided:

```{r}
unique(TripDaten$DATE)
```

**START_TIME** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r timecolumn2, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$STARTTIME))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for TIME. Format expected (hh:mm:ss). Format provided

```{r}
unique(TripDaten$STARTTIME,na.rm=TRUE)
```

**END_TIME** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r timecolumn3, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$ENDTIME))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for TIME. Format expected (hh:mm:ss). Format provided:

```{r}
unique(TripDaten$ENDTIME,na.rm=TRUE)
```

**STRIP_WIDTH** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$STRIP_WIDTH))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for STRIP_WIDTH

```{r}
unique(TripDaten$STRIP_WIDTH)
```

**AREA_ANALYSED** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$AREA_ANALYSED))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for AREA_ANALYSED

```{r}
unique(TripDaten$AREA_ANALYSED)
```

**AREA_CONTROLLED** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(TripDaten$AREA_CONTROLLED))/nrow(TripDaten),1),"%","missing values",sep=" "))
```

Values provided for AREA_CONTROLLED  

```{r}
unique(TripDaten$AREA_CONTROLLED)
```

#  2. BasisDaten

```{r PosFolder, include=F, echo=FALSE}
BasisDaten
BasisDatenColumns<-colnames(BasisDaten)
```

```{r, include=F, echo=FALSE}
BasisDatenExpectedColumns<-c("POSITIONS","POSITION_ID","POSITION_ID_CONTROLLED", "Dataset_ID","TRIP_ID","CRUISENO","CAMERA_NUMBER","TRANSECT_NUMBER","DATE","TIME","LAT_PIC_CENTER","LON_PIC_CENTER","PLANE_FLIGHT_HEIGHT","PIC_AREA_ANALYSED","GLARE","SEASTATE","TURBIDITY","ICE","CLARITY","PIC_QUALITY","PIC_FILENAME","NOTES")
```

In this part we would check that all the columns are correctly imported.

```{r,error=TRUE, comment=NA, include=TRUE, echo=FALSE}
cat(paste('The Basisdaten contains',nrow(BasisDaten),'rows, and',ncol(BasisDaten),'columns.'))
cat(paste('The columns names are: '))
cat(colnames(BasisDaten))
```

## Column checks

```{r Check columns2, include=T, echo=F, comment=NA}
cat(paste('\n Expected',length(BasisDatenExpectedColumns),'columns and',ncol(BasisDaten),'provided', sep=" "))
```

```{r, echo=FALSE}
ExpectedColumns<-BasisDatenExpectedColumns
ProvidedColumns<-colnames(BasisDaten)
MaxColumns <- max(length(ExpectedColumns), length(ProvidedColumns))
length(ExpectedColumns) <- MaxColumns                      
length(ProvidedColumns) <- MaxColumns
ExpectedColumns<-data.frame(name=c(ExpectedColumns),expected=ExpectedColumns)
ProvidedColumns<-data.frame(name=c(ProvidedColumns),provided=ProvidedColumns)
ComparisonColumns<-merge(ExpectedColumns,ProvidedColumns,by='name',all=TRUE)
colnames(ComparisonColumns)<-c('Name','Expected','Provided')
ComparisonColumns<-ComparisonColumns %>% drop_na(Name)
```

```{r, echo=FALSE}
ComparisonBasisDaten<-ComparisonColumns %>% dplyr::select(Expected,Provided)
colnames(ComparisonBasisDaten)<-c("Expected","Provided")
```

Values **NA** indicate if the columns were provided or are missing. 

```{r TableColBasis, echo=FALSE}
knitr::kable(ComparisonBasisDaten)
```


Missing columns include:

```{r}
if((nrow(ComparisonBasisDaten %>%
  filter(is.na(Provided)))>0)==FALSE){
         cat(("There are no missing columns"))
        }else{knitr::kable(ComparisonBasisDaten %>%
  filter(is.na(Provided)))}
```

**POSITION_ID** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$POSITION_ID))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided:

```{r}
range(BasisDaten$POSITION_ID)
```


**POSITION_ID_CONTROLLED** is not a mandatory field. There can be missing values.

```{r, include=T,comment=NA}
if ("POSITION_ID_CONTROLLED" %in% colnames(BasisDaten)) {
  # Column exists
  cat(paste(round(100*sum(is.na(BasisDaten$POSITION_ID_CONTROLLED))/nrow(BasisDaten),1),"%","missing values",sep=" "))
} else {
  # Column does not exist
  print("Column POSITION_ID_CONTROLLED is missing. Check names of the columns. ")
}
```

Enter if an image has been controlled during the screening control = 1, ID control = 2, or during both working steps = 3.

```{r}
if ("POSITION_ID_CONTROLLED" %in% colnames(BasisDaten)) {
  # Column exists
  unique(BasisDaten$POSITION_ID_CONTROLLED,na.rm=TRUE)
} else {
  # Column does not exist
  print("Column POSITION_ID_CONTROLLED_is missing. Check names of the columns. ")
}
```

**DATE** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$DATE))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for DATE. Format expected (YYYYMMDD). Format provided:

```{r}
unique(BasisDaten$DATE,na.rm=TRUE)
```

**TIME** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r timecolumn, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$TIME))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for TIME. Format expected (hh:mm:ss). Format provided

```{r}
range(BasisDaten$TIME,na.rm=TRUE)
```

**LAT_PIC_CENTER** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$LAT_PIC_CENTER))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```
Values provided:

```{r}
range(BasisDaten$LAT_PIC_CENTER)
```

**LON_PIC_CENTER** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$LON_PIC_CENTER))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided:

```{r}
range(BasisDaten$LON_PIC_CENTER)
```

**PLANE_FLIGHT_HEIGHT** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$PLANE_FLIGHT_HEIGHT))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for PLANE_FLIGHT_HEIGHT. Variation is expected.

```{r}
range(BasisDaten$PLANE_FLIGHT_HEIGHT)
```

**PIC_AREA_ANALYSED** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$PIC_AREA_ANALYSED))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for PIC_AREA_ANALYSED. Variation is expected. 

```{r}
range(BasisDaten$PIC_AREA_ANALYSED)
```

## Environmental conditions during the surveys

**GLARE** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$GLARE))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for GLARE. Values 0 to 3 are allowed. 

```{r}
unique(BasisDaten$GLARE)
```

**SEASTATE** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$SEASTATE))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for SEASTATE. Values 0 to 7 are allowed. 

```{r}
unique(BasisDaten$SEASTATE)
```

**TURBIDITY** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$TURBIDITY))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for TURBIDITY. Only 1 to 3 are allowed. 

```{r}
unique(BasisDaten$TURBIDITY)
```

**CLARITY** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$CLARITY))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for CLARITY. Only 0 to 3 are allowed. 

```{r}
unique(BasisDaten$CLARITY)
```

**PIC_QUALITY** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(BasisDaten$PIC_QUALITY))/nrow(BasisDaten),1),"%","missing values",sep=" "))
```

Values provided for PIC_QUALITY. Only 1 and 2 are allowed. 

```{r}
range(BasisDaten$PIC_QUALITY)
```

# 3.Observations

```{r ObsFolder, include=F, echo=FALSE}
ObservationsColumns<-colnames(Observations)
```

```{r, include=F, echo=FALSE}
ObservationsExpectedColumns<-c("OBSERVATIONS","OBSERVATION_ID","POSITION_ID","Dataset_ID","CRUISENO",
                               "ABIOTIC_STRUCTURES","ABIOTIC_OBSERVATION","OBSERVATION",
                               "ENGLISH_NAME_BEFORE_CONTROL","ENGLISH_NAME_CONTROL_ID",
                               "ID_MATCH_MISMATCH","ENGLISH_NAME","DETECTION_STEP","BEHAVIOUR",
                               "ACTIVITY","GROUP","FAMILY_GROUP","ASSOCIATIONS","HEADING","SUBMERGED",
                               "AGE_CLASS","AGE_YEARS","PLUMAGE","SEX","LENGTH","WING_SPAN",
                               "FLIGHT_HEIGHT","FLIGHT_HEIGHT_CONFIDENCE","FLIGHT_HEIGHT_METHOD_ID",
                               "LAT_OBJECT","LON_OBJECT","NOTES")
```

In this part we would check that all the columns are correctly imported.

```{r,error=TRUE, comment=NA, include=TRUE, echo=FALSE}
cat(paste('The Observations contains',nrow(Observations),'rows, and',ncol(Observations),'columns.'))
cat(paste('The columns names are: '))
cat(colnames(Observations))
```

## Column checks

```{r Check columns3, include=T, echo=F, comment=NA}
cat(paste('\n Expected',length(ObservationsExpectedColumns),'columns and',ncol(Observations),'provided', sep=" "))
```

```{r, echo=FALSE}
ExpectedColumns<-ObservationsExpectedColumns
ProvidedColumns<-colnames(Observations)
MaxColumns <- max(length(ExpectedColumns), length(ProvidedColumns))
length(ExpectedColumns) <- MaxColumns                      
length(ProvidedColumns) <- MaxColumns
ExpectedColumns<-data.frame(name=c(ExpectedColumns),expected=ExpectedColumns)
ProvidedColumns<-data.frame(name=c(ProvidedColumns),provided=ProvidedColumns)
ComparisonColumns<-merge(ExpectedColumns,ProvidedColumns,by='name',all=TRUE)
colnames(ComparisonColumns)<-c('Name','Expected','Provided')
ComparisonColumns<-ComparisonColumns %>% drop_na(Name)
ComparisonObservations<-ComparisonColumns %>% dplyr::select(Expected,Provided)
colnames(ComparisonObservations)<-c("Expected","Provided")
```

Values **NA** indicate if the columns were provided or are missing. 

```{r TableObs, echo=FALSE}
knitr::kable(ComparisonObservations)
```

Missing columns include:

```{r}
if((nrow(ComparisonObservations %>%
  filter(is.na(Provided)))>0)==FALSE){
         cat(("There are no missing columns"))
        }else{knitr::kable(ComparisonObservations %>%
  filter(is.na(Provided)))}
```

**OBSERVATION_ID** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
if ("OBSERVATION_ID" %in% colnames(Observations)) {
  # Column exists
  cat(paste(round(100*sum(is.na(Observations$OBSERVATION_ID))/nrow(Observations),1),"%","missing values",sep=" "))
} else {
  # Column does not exist
  print("Column OBSERVATION_ID is missing. Check names of the columns. ")
}
```

Values provided for OBSERVATION_ID

```{r}
Observations$OBSERVATION_ID<-as.numeric(Observations$OBSERVATION_ID)
range(Observations$OBSERVATION_ID,na.rm=TRUE)
```

**POSITION_ID** is a mandatory field. There must be 0% missing values, otherwise please check. 

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(Observations$POSITION_ID))/nrow(Observations),1),"%","missing values",sep=" "))
```

Values provided for POSITION_ID.

```{r}
Observations$POSITION_ID<-as.numeric(Observations$POSITION_ID)
range(Observations$POSITION_ID,na.rm=TRUE)
```

**OBSERVATION** is a mandatory field, but there might be missing values if there are **ABIOTIC_OBSERVATION** or **ABIOTIC_STRUCTURE**.

```{r, include=T,comment=NA}
cat(paste(round(100*sum(is.na(Observations$OBSERVATION))/nrow(Observations),1),"%","missing values",sep=" "))
```

Number of values missing: 

```{r}
sum(is.na(Observations$OBSERVATION))
```

Number of **ABIOTIC_STRUCTURE** observations.

```{r, include=T,comment=NA}
cat(paste(round(((Observations %>%
  drop_na(ABIOTIC_STRUCTURES)%>%
  count())$n)),"values in ABIOTIC_STRUCTURES",sep=" "))
```

Number of **ABIOTIC_OBSERVATION** observations.

```{r, include=T,comment=NA}
cat(paste(((Observations %>%
  drop_na(ABIOTIC_OBSERVATION)%>%
  count())$n)),"values in ABIOTIC_OBSERVATION",sep=" ")
```

Values provided in ABIOTIC_STRUCTURES.

```{r}
unique(Observations$ABIOTIC_STRUCTURES,na.rm=TRUE)
```

Values provided in ABIOTIC_OBSERVATION.

```{r}
unique(Observations$ABIOTIC_OBSERVATION,na.rm=TRUE)
```

**ID_MATCH_MISMATCH** is a not mandatory field. There can be missing values.

```{r, include=T,comment=NA}
if("ID_MATCH_MISMATCH" %in% colnames(Observations)){
         cat(paste(round(100*sum(is.na(Observations$ID_MATCH_MISMATCH))/nrow(Observations),1),"%","missing values",sep=" "))
        }else{  
          print(paste0("The column ID_MATCH_MISSMATCH is missing"))
           }
```

Values provided in **ID_MATCH_MISMATCH**. 1 = Matches between the identifier and the auditor, 2 = Mismatches between identifier and the auditor. 

```{r}
unique(Observations$ID_MATCH_MISMATCH,na.rm=TRUE)
```

**BEHAVIOUR** is not mandatory field. Values are presented as numerical codes.

```{r}
unique(Observations$BEHAVIOUR)
```

**ACTIVITY** is not mandatory field. Values should be 1 = Swimming, 2 = Flying, 3 = Submerged, 4 = Breaching surface, 5 = On artificial platform, 0 = Unknown. 0s are only allowed for abiotic structures.

```{r}
unique(Observations$ACTIVITY)
```

**GROUP** is not mandatory field. Values should be Consecutive number of groups; same number for all individuals of the same group.

```{r}
unique(Observations$GROUP)
```

**ASSOCIATIONS** is not mandatory field. Values are presented as numerical codes.

```{r}
unique(Observations$ASSOCIATIONS)
```

**HEADING** is not mandatory field. Values should be 45, 90, 135, 180, 225, 270, 315, 360.

```{r}
unique(Observations$HEADING)
```

**SUBMERGE** is not mandatory field. If filled values should be o,u,x.

```{r}
unique(Observations$SUBMERGED)
```

**AGE_CLASS** is not mandatory field. If filled values should be age of the bird; A (adult), IM (immature). 

```{r}
unique(Observations$AGE_CLASS)
```

**AGE_YEARS** is not mandatory field. If filled values should be numeric. Specification of the calender-year of the bird. 
Values expected 1 to 5.

```{r}
unique(Observations$AGE_YEARS)
```

**SEX** is not mandatory field. If filled values should be F or M.  

```{r}
unique(Observations$SEX)
```

**LON_OBJECT** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
Observations$LON_OBJECT<-as.numeric(Observations$LON_OBJECT)
cat(paste(round(100*sum(is.na(Observations$LON_OBJECT))/nrow(Observations),1),"%","missing values",sep=" "))
```

Values should be numerical. 

```{r}
range(Observations$LON_OBJECT)
```

**LAT_OBJECT** is a mandatory field. There must be 0% missing values, otherwise please check.

```{r, include=T,comment=NA}
Observations$LAT_OBJECT<-as.numeric(Observations$LAT_OBJECT)
cat(paste(round(100*sum(is.na(Observations$LAT_OBJECT))/nrow(Observations),1),"%","missing values",sep=" "))
```

Values should be numerical. 

```{r}
range(Observations$LAT_OBJECT)
```

## English names

List all **species** sighted during the surveys with number of sightings and check the codes.

```{r SpeciesList, echo=FALSE, comment=NA}
Names_1check<-Observations %>% drop_na(OBSERVATION)
Names_2check<-Names_1check %>% 
    group_by(ENGLISH_NAME,OBSERVATION) %>%
   count()
Names_2check<-Names_2check%>% arrange(as.numeric(OBSERVATION))

Euring<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)%>%
  mutate(Code=as.numeric(Code))%>%
  select(Code,ENGLISH_NAME)%>%
  # update Arctic Tern Code
  mutate(Code=case_when(Code==6169~6159,TRUE ~ Code))

Names_3check<-Names_2check %>%
  mutate(Code=as.numeric(OBSERVATION))%>%
  left_join(Euring,by='Code')%>%
  rename(ENGLISH_NAME_provided=ENGLISH_NAME.x,
         ENGLISH_NAME_expected=ENGLISH_NAME.y)%>%
  mutate(check=(ENGLISH_NAME_provided==ENGLISH_NAME_expected))%>%
  relocate(Code,OBSERVATION,ENGLISH_NAME_expected, ENGLISH_NAME_provided,n)%>%
  rename('Code provided'=OBSERVATION,
         'Code expected'=Code,
         'Name provided'=ENGLISH_NAME_provided,
         'Name expected'=ENGLISH_NAME_expected,
         'Name fitting'=check)

Names_4check<-Names_3check %>%
  select('Code provided','Name provided','Name fitting',n)

knitr::kable(Names_4check)
```



Often names are not equal as there is no space between the diagonals (e.g.  seal / small cetacean provided and  seal/small cetacean expected) or missing a word (e.g. Red-necked/Great Crested Grebe provided and Red-necked Grebe/Great Crested Grebe expected, the word Grebe is missing). 

```{r CodesInternalCheck, echo=FALSE}
# Check names not fitting
if (nrow(filter(Names_3check, `Name fitting` == FALSE)) == 0) {
  cat("There are no missing names")
} else {
    cat("Please correct the following names")
  knitr::kable(
  Names_3check %>%
    filter(`Name fitting` == FALSE)%>%
  select('Code provided','Code expected','Name provided','Name expected','Name fitting',n)
  )
}
```

Check that all species names are part of a morphological/taxonomic group. Otherwise they wont be plotted in the maps in the Plausability Check. Usually the problem is that the name doesnt fit the Euring. 

```{r CodesTax, echo=FALSE}
Euring_Tax<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)%>%
  mutate(Code=as.numeric(Code))%>%
  select(Code,ENGLISH_NAME,Artificial_tax_class)%>%
  # update Arctic Tern Code
  mutate(Code=case_when(Code==6169~6159,TRUE ~ Code))

Names_4tax<- subset(Names_1check, OBSERVATION != "0")
Names_5tax<-left_join(Names_4tax,Euring_Tax,by='ENGLISH_NAME')
Names_6taxmissing<-Names_5tax %>% 
  filter(is.na(Artificial_tax_class))

Names_7taxmissing<-Names_6taxmissing %>% 
  group_by(ENGLISH_NAME,Artificial_tax_class)%>% 
  tally()

# Check names not fitting
if (length(unique(Names_7taxmissing$ENGLISH_NAME)) == 0) {
  cat("There are no species missing tax/morphological classification.")
} else {
  cat("These species are missing tax/morphological classification.")
  knitr::kable(Names_7taxmissing)
}
```


***End of the document. ***
