---
title: "PlausabilityCheck"
author: "MarBird"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
params:
  ThisDirectory: ThisDirectory
  ThisFile: ThisFile
  TripDaten: TripDaten
  BasisDaten: BasisDaten
  Observations: Observations
---


# Intro

Using data from **`r params$ThisFile`** excel file.  
The present document imports and explores the data provided.

In this document you will find:  
1. Revision of **control steps**. Including Area observed, Area controlled.  
2. Revision of **survey area**. Including a map of the surveyed area.
3. Revision of **environmental conditions**. Visualization of environmental conditions during the survey.  
4. Revision of **Observations**. Including species list, check that the codes correspond to the species name, check the proportion of birds and mammals, check the most common species observed during the survey. Check errors in identifications.  
5. Revision of **Plausibility** in the columns Activity, Age class and Sex.  
6. **Spatial distribution** per taxonomic/morphological groups.  

```{r PackageNames, echo=FALSE,message=FALSE, warning=FALSE}
#LAST UPDATE 2025-06-16
PackageList<-c('sp','dplyr','ggplot2','beepr','sf','readxl','tmap','seamonas','kableExtra') 
LoadPackages<-function(x){sapply(x, require, character.only = TRUE)}
```

```{r LoadPackages, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
LoadPackages(PackageList)
```

```{r use_params,echo=FALSE, echo=FALSE}
Plausability_Trip<-params$TripDaten
Plausability_Basis<-params$BasisDaten
Plausability_Observations<-params$Observations
```

```{r ManualEdit,echo=FALSE, eval=FALSE}
Plausability_Trip<-TripDaten
Plausability_Basis<-BasisDaten
Plausability_Observations<-Observations
```

\newpage

# Control steps

## Survey info

Surveys must avoid noon due to problems with glare. Condition is that the transect width must be at least 400 m.

```{r TableStripWidth, echo=FALSE}
Table_Survey<-Plausability_Trip %>%
  dplyr::select(TRIP_ID,DATE,STARTTIME,ENDTIME,STRIP_WIDTH)%>%
  mutate(CONDITION=case_when(STRIP_WIDTH >= 400 ~ "Reached (400m)",
                             TRUE ~ "Not reached (400m)"))
Table_Survey <- flextable(Table_Survey)
# Set column widths manually (in inches)
Table_Survey<- set_table_properties(Table_Survey, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   
  width(j = 2, width = 1.5) %>% 
  width(j = 3, width = 1.2)     
# Print table 
Table_Survey
```

## Area observed

What was the proportion of **area analysed** in relation to the **area observed**?
A minimum proportion of 70% of the recorded images or videos must be analyzable. Otherwise surveys must be repeated (at company's expenses). 

```{r TableAreas,echo=FALSE}
Table_Areas <- data.frame(survey_dates = as.character(unique(Plausability_Trip$DATE)),
                         area_observed = sum(Plausability_Trip$AREA_OBSERVED),
                         area_analysed= sum(Plausability_Trip$AREA_ANALYSED))
Table_Areas<-Table_Areas %>%
  mutate(area_proportion = round(((area_analysed*100)/area_observed),2))%>%
  mutate(CONDITION=case_when(area_proportion > 70 ~ "Reached (70%)",
                             TRUE ~ "Not reached (70%)"))
names(Table_Areas) <- c("survey dates (YYYYMMDD)","area observed [km^2]","area analysed [km^2]","Proportion [%]","CONDITION")
Table_Areas<- flextable(Table_Areas)
Table_Areas <- set_table_properties(Table_Areas, width = 1, layout = "autofit")%>%
  width(j = 1, width = 2) %>%   
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2)  %>% 
  width(j = 4, width = 2)      
# Print table 
Table_Areas
```

## Area controlled

What was the **area analysed** and the **area controlled** (i.e. area controlled during the screening control) in relation to the area analysed?

Area controlled should be > 20%. 

```{r TableControlled, echo=FALSE, eval=TRUE}
Table_Controlled <- data.frame(survey_dates = as.character(Plausability_Trip$DATE),
                          area_analysed = as.numeric(Plausability_Trip$AREA_ANALYSED),
                          area_controlled= as.numeric(Plausability_Trip$AREA_CONTROLLED),
                          area_controlled_prop =  NA)%>%
  mutate(area_controlled_prop = round((area_controlled / area_analysed) * 100, 2)
  )
Table_Controlled<-Table_Controlled %>%
    mutate(CONDITION=case_when(area_controlled_prop > 20 ~ "Reached (20%)",
                             TRUE ~ "Not reached (20%)"))
names(Table_Controlled) <- c("survey dates (YYYYMMDD)","area analysed [km^2]","area controlled [km^2]","area controlled [%]","CONDITION")
Table_Controlled<- flextable(Table_Controlled)
Table_Controlled<- set_table_properties(Table_Controlled, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2)  %>% 
  width(j = 4, width = 2) %>% 
  width(j = 5, width = 2) 
Table_Controlled
```


\newpage

# Survey flight

## Maps of the survey effort

Season surveyed.  

```{r, echo=FALSE}
Season<-Plausability_Basis %>%
  mutate(month=substr(DATE,5,6))%>%
  mutate(season=case_when(month %in% c("12","01","02") ~ "winter", #DEC, JAN, FEB
                          month %in% c("03","04","05") ~ "spring", #MAR, APR, MAY
                          month %in% c("06","07","08") ~ "summer", #JUN, JUL, AGO
                          month %in% c("09","10","11") ~ "autumn", #SEP, OCT, NOV
                          FALSE~"u"))
unique(Season$season)
```

The **spatial extent** of the survey.

```{r SurveyMap,echo=FALSE, fig.width=6}
Study_areas<-st_transform(GermanNorthSea::Study_areas,4326)
Protected_SCA<- st_transform(GermanNorthSea::German_SCA,4326)
Land<- st_transform(GermanNorthSea::German_land,4326)
Protected_natura <- st_transform(GermanNorthSea::German_natura,4326)

Basis_df<-fortify(Plausability_Basis)
Basis_df$lat<-as.numeric(Basis_df$LAT_PIC_CENTER)
Basis_df$lon<-as.numeric(Basis_df$LON_PIC_CENTER)
Basis_df <- Basis_df[!is.na(Basis_df$lat) & !is.na(Basis_df$lon), ]
Basis_sf <- st_as_sf(Basis_df, coords = c("lon", "lat"),crs = 4326, agr = "constant")

ggplot(data = Basis_sf) +
  geom_sf(data = Study_areas, aes(fill=stratum),
          colour = 'black', alpha=0.1)+
  scale_fill_manual(values = c(A = '#7400b8',B = '#6930c3',C = '#5e60ce',
                               D = '#277da1',E = '#577590',F = '#4d908e',
                               G = '#43aa8b',H = '#90be6d',I = '#f9c74f',
                               J = '#ff6d00',K = '#f8961e',L = '#f3722c',
                               N = '#f94144'))+
  geom_point(data = Basis_df, 
                aes(x = lon, y = lat), 
                size = 1, shape = 21, colour = "#9d0208")+
  geom_sf(data = Land, colour = 'black', fill = '#e5e5e5')+
  coord_sf(xlim = c(3, 15), ylim = c(53, 56), expand = FALSE)+
  theme_bw()+
  xlab('Longitude')+ylab('Latitude')+
  theme(axis.text = element_text(size=6),
        axis.title.x = element_text(size=6),
        axis.title.y = element_text(size=6),
        legend.position='none')+
  scale_x_continuous(labels = function(x) paste0(x, '\u00B0', "W")) +
  scale_y_continuous(labels = function(x) paste0(x, '\u00B0', "N")) 
```

## Plane height

Some variation in plane height during the survey is expected. 

```{r FlightHeightPlot, echo=F, fig.width=10, fig.height=3, warning=FALSE}
ggplot(data=Plausability_Basis,aes(x=POSITION_ID,y=PLANE_FLIGHT_HEIGHT),color=CAMERA_NUMBER)+
    geom_point(aes(colour = factor(PLANE_FLIGHT_HEIGHT)), size = 1,color='darkblue') +
    xlab("Picture_ID")+ylab('Plane height')+
  theme_classic()+ 
  theme(axis.title = element_text(size=15),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size=15),
        legend.position='none')+
  scale_x_discrete(limits=Plausability_Basis$POSITION_ID,breaks=Plausability_Basis$POSITION_ID[seq(1,length(Plausability_Basis$POSITION_ID),by=5000)])+
  theme(axis.text.x = element_text(angle=90,size=8))
```

\newpage

# Environmental conditions during the surveys

The conditions are plotted with the x axis being the POSITION_ID and the y axis the conditions.  
For each POSITION_ID, all cameras are plotted but are one on top of the other. Therefore, the cameras will only be noticeable if the camera report different conditions for the same POSITION_ID.  
The name of the all POSITION_ID is not plotted as it is no legible, but every 5,000 are plotted to use as a reference.

```{r WeatherPlotFunction, echo=F, eval=T}
PlotConditions<-function(EjeY=EjeY){
  
  Plausability_Basis$EjeX<-Plausability_Basis$POSITION_ID

  ggplot(data=Plausability_Basis,aes(x=EjeX,y=EjeY),color=CAMERA_NUMBER)+
    geom_point(aes(colour = factor(EjeY)), size = 1) +
    xlab("Picture_ID")+
  theme_classic()+ 
  theme(axis.title = element_text(size=15),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size=15),
        legend.position='none')+
  scale_x_discrete(limits=Plausability_Basis$EjeX,
                   breaks=Plausability_Basis$EjeX[seq(1,length(Plausability_Basis$EjeX),
                                                      by=5000)])+
  theme(axis.text.x = element_text(angle=90,size=8))
}
```

## Glare
Intensity of the reflection of the sun in regular intervals and after a change of direction or transect, ascertained for the analysed part of the image. Defined as 0 = No glare, 1 = low glare, 2 = medium glare, 3 = strong glare.

```{r GlarePlot, echo=F, fig.width=10, fig.height=3, warning=FALSE}
PlotConditions(EjeY=as.numeric(Plausability_Basis$GLARE))+
  ylab("Glare")+
  scale_y_continuous(limits=c(-0.5,3))+ 
  scale_color_manual(values=c("0"="#457b9d",
                              "1"="#457b9d",
                              "2"="#457b9d",
                              "3"="#e63946", 
                              "1.5"="#fb8500",
                              "2.5"="#fb8500"))
```

## Sea state
Sea state classification goes from 0 to 7.  Values <3 in blue, values > 3 in red. Usually no flights are performed above 3. 

```{r SeastatePlot, echo=F, fig.width=10, fig.height=4.5, warning=FALSE}
PlotConditions(EjeY=as.numeric(Plausability_Basis$SEASTATE))+
  ylab("Sea state")+
  scale_y_continuous(expand = c(0,0),limits=c(-0.5,7.5), breaks=c(0,1,2,3,4,5,6,7))+
  scale_color_manual(values=c("0"="#457b9d", #0
                              "1"="#457b9d", #1
                              "2"="#457b9d", #2 
                              "3"="#457b9d", #3 blue
                              "4"="#e63946", #4 red
                              "5"="#e63946", #5
                              "6"="#e63946", #6
                              "7"="#e63946"))#7
```

\newpage

## Turbidity
Turbidity goes from 1-3. Classification corresponds to: 1= no turbidity, 2= medium turbidity, 3=strong turbidity. Note: 0 is not allowed and is shown is marked in red. 

```{r TurbidityPlot, echo=F, fig.width=10, fig.height=4.5, warning=FALSE}
PlotConditions(EjeY=as.numeric(Plausability_Basis$TURBIDITY))+
  ylab("Turbidity")+
  scale_y_continuous(limits=c(-0.5,3.5),breaks=c(0,1,2,3)) +
  scale_color_manual(values=c("0"="#e63946", #red
                              "1"="#457b9d", #blue
                              "2"="#457b9d",
                              "3"="#457b9d"))
```

## Clarity
Clarity of the air goes from: 0 = not recorded, 1 = little, 2 = medium, 3 = strong. 

```{r ClarityPlot, echo=F, fig.width=10, fig.height=3, warning=FALSE}
PlotConditions(EjeY=as.numeric(Plausability_Basis$CLARITY))+
  ylab("Clarity of air")+
  scale_y_continuous(limits=c(0,3))+
  scale_color_manual(values=c("0"="#e63946",
                              "1"="#457b9d", 
                              "2"="#457b9d",
                              "3"="#457b9d"))
```

\newpage

## Picture quality

What is the proportion of pictures that had **good quality**.  Is expected to be above 80%. 

```{r TablePicture, echo=FALSE,eval=TRUE}
FlightName<-unique(Plausability_Basis$CRUISENO)
GoodQuality<-Plausability_Basis%>%
  filter(PIC_QUALITY==1)%>%
  tally()
BadQuality<-Plausability_Basis%>%
  filter(PIC_QUALITY==2)%>%
  tally()
Table_Picture<- data.frame(survey = FlightName,
                           good_quality = GoodQuality$n,
                           bad_quality = BadQuality$n)
Table_Picture<-Table_Picture %>%
  mutate(pic_quality_percent = (good_quality*100)/(good_quality+bad_quality))
Table_Picture<- Table_Picture %>%
  mutate(CONDITION=case_when(pic_quality_percent > 80 ~ "Reached (80%)",
                             TRUE ~ "Not reached (80%)"))
names(Table_Picture) <- c("survey",
                          "Good (n)",
                          "Bad (n)",
                          "Percentage good quality [%]",
                          "CONDITION")
Table_Picture <- flextable(Table_Picture)
# Set column widths manually (in inches)
Table_Picture<- set_table_properties(Table_Picture, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   # column 1 = 2 inches
  width(j = 2, width = 1.5) %>% 
  width(j = 3, width = 1.5) %>% 
  width(j = 4, width = 2) %>% 
  width(j = 5, width = 2) 
# Print table 
Table_Picture
```

Picture quality classification corresponds to: 1= the image has been analysed, 2= image quality too bad for analysis (in red).

```{r PicturePlot, echo=F, fig.width=10, fig.height=3, warning=FALSE}
Plausability_Basis$PIC_QUALITY<-as.numeric(Plausability_Basis$PIC_QUALITY)
PlotConditions(EjeY=Plausability_Basis$PIC_QUALITY)+
  ylab("Picture quality")+
  scale_y_continuous(limits=c(0,3),breaks=c(0,1,2,3))+ 
  scale_color_manual(breaks = c("1", "2"),
                     values=c("0"="#457b9d",
                              "1"="#457b9d", #blue
                              "2"="#e63946")) #red
```

\newpage

# Observations

## Species densities

Check densities being plausible.  Note that for number of species, unidentified individuals were counted as one species.  

```{r TableDensities,  echo=FALSE, eval=TRUE}
Table_Densities<-data.frame(Number_species=(Observations %>%
                             distinct(ENGLISH_NAME)%>%
                             drop_na(ENGLISH_NAME)%>%
                             count())$n,
           Number_individuals=(Observations %>%
                                 drop_na(ENGLISH_NAME)%>%
                                 count())$n,
           Area_analysed=sum(TripDaten$AREA_ANALYSED)
           )
Table_Densities<-Table_Densities %>%
  mutate(Densities=round(Number_individuals/Area_analysed,2))%>%
  rename('Total no. of species sighted'=Number_species,
         'Total no. of individuals'=Number_individuals,
         'Area analysed [km2]'=Area_analysed,
         'Density [ind/km2]'=Densities)
Table_Densities<- flextable(Table_Densities)
Table_Densities <- set_table_properties(Table_Densities, width = 1, layout = "autofit")
Table_Densities
```

## Controlled sightings per survey

How large was the difference between ID and the ID control (**ID_CONTROL_DIFFERENCE**)?

```{r ControlledIDObservations,echo=FALSE, include=FALSE}
# Total number of sightings from Observations
Controlled_Observations<-Plausability_Observations %>%
  left_join(BasisDaten,by='POSITION_ID') %>%
  group_by(DATE)%>%
  tally()
Controlled_Observations <-Controlled_Observations %>% 
  rename(survey_dates_YYYYMMDD=DATE,
         number_of_sightings=n)

# Number of controlled sightings, from Trip
Controlled_Ids<- Plausability_Observations %>%
  group_by(ID_MATCH_MISMATCH)%>%
  tally()
Controlled_Ids<- Controlled_Ids[2,2]+Controlled_Ids[1,2]
Controlled_Ids <- Controlled_Ids %>% rename(number_of_controlled_sightings=n)

# Difference between match and mismatch
Controlled_Ids_Difference<-Plausability_Observations %>%
  group_by(ID_MATCH_MISMATCH)%>%
  tally()
Controlled_Difference <- Controlled_Ids_Difference$n[2]*100/ (Controlled_Ids_Difference$n[1]+Controlled_Ids_Difference$n[2])
Controlled_Difference
```

```{r ControlledIDTable, echo=FALSE, include=FALSE}
Controlled_Observations_Table<-cbind(Controlled_Observations,Controlled_Ids)
Controlled_Observations_Table<- Controlled_Observations_Table %>% 
  mutate(Id_controlled_difference=Controlled_Difference)%>%
  mutate(percentaje_of_controlled=number_of_controlled_sightings*100/number_of_sightings)%>%
  mutate(percentaje_of_controlled=round(percentaje_of_controlled,2))
Controlled_Observations_Table 
```

```{r Controlled_Table, echo=FALSE}
Controlled_Table<-Controlled_Observations_Table  %>%
  relocate(survey_dates_YYYYMMDD,
           number_of_sightings,
           number_of_controlled_sightings,
           Id_controlled_difference,
           percentaje_of_controlled)
```

```{r ControlledTableNames,echo=FALSE}
names(Controlled_Table)<- c("survey dates (YYYYMMDD)",
                           "number of sightings",
                           "number of controlled sightings",
                           "difference between first ID and control [%]",
                           "percentage of controlled sightings [%]")
```

```{r ControlledTableKnitr, echo=FALSE, eval=TRUE}
Controlled_Table<- flextable(Controlled_Table)
Controlled_Table <- set_table_properties(Controlled_Table, width = 1, layout = "autofit")
Controlled_Table
```

\newpage

# Abiotic structures

```{r TableAbioticStructures, echo=FALSE}
if (nrow(Observations %>% filter(!is.na(ABIOTIC_STRUCTURES))) == 0) {
  print("There were no ABIOTIC_STRUCTURES")
        }else{  
          Abiotic_Structures<-Plausability_Observations %>%
            drop_na(ABIOTIC_STRUCTURES)%>%
            group_by(ABIOTIC_STRUCTURES)%>%
            count()
          Abiotic_Descriptions<-seamonas::Code_Descriptions %>%
            select(starts_with("ABIOTIC_STRUCTURE"))%>%
            rename(ABIOTIC_STRUCTURES=ABIOTIC_STRUCTURE_CODE)%>%
            mutate(ABIOTIC_STRUCTURES=as.character(ABIOTIC_STRUCTURES))%>%
            drop_na()
          Abiotic_Structures <-Abiotic_Structures %>%
            mutate(ABIOTIC_STRUCTURES=as.character(ABIOTIC_STRUCTURES))%>%
            left_join(Abiotic_Descriptions,by='ABIOTIC_STRUCTURES')%>%
            drop_na()%>%
            select(ABIOTIC_STRUCTURES,ABIOTIC_STRUCTURE_DESCRIPTION,n)
Abiotic_Structures<- flextable(Abiotic_Structures)
Abiotic_Structures<- set_table_properties(Abiotic_Structures, width = 1, layout = "autofit") 
Abiotic_Structures
          }
```

# Abiotic observations

```{r TableAbioticObservations, echo=FALSE}
if (nrow(Plausability_Observations %>% filter(!is.na(ABIOTIC_OBSERVATION))) == 0) {
  print(paste0("There were no ABIOTIC_OBSERVATION"))
}else{  
  Abiotic_Observations<-Plausability_Observations %>%
    drop_na(ABIOTIC_OBSERVATION)%>%
    group_by(ABIOTIC_OBSERVATION)%>%
    count()
  AbioticObs_Descriptions<-seamonas::Code_Descriptions %>%
    select(starts_with("ABIOTIC_OBSERVATIO"))%>%
    rename(ABIOTIC_OBSERVATION=ABIOTIC_OBSERVATION_CODE)%>%
    mutate(ABIOTIC_OBSERVATION=as.character(ABIOTIC_OBSERVATION))%>%
    drop_na()
  Abiotic_Observations <-Abiotic_Observations %>%
    mutate(ABIOTIC_OBSERVATION=as.character(ABIOTIC_OBSERVATION))%>%
    left_join(AbioticObs_Descriptions,by='ABIOTIC_OBSERVATION')%>%
    drop_na()%>%
    select(ABIOTIC_OBSERVATION,ABIOTIC_OBSERVATION_DESCRIPTION,n)
    
Abiotic_Observations<- flextable(Abiotic_Observations)
Abiotic_Observations<- set_table_properties(Abiotic_Observations, width = 1, layout = "autofit") 
Abiotic_Observations
}
```


<br>

```{r AbioticObservations, echo=FALSE, comment=NA, message=FALSE}
#Create a column with mammal or birds
sprintf("Note: %d abiotic structures and abiotic observations that will not be included in the next steps",length(which(is.na(Plausability_Observations$OBSERVATION))))
```
\newpage

# Species list

List all **species** sighted during the surveys with number of sightings and check the codes.

```{r Species_Table, echo=FALSE}
Names_1check<-Observations %>% drop_na(OBSERVATION)
Names_2check<-Names_1check %>% 
    group_by(ENGLISH_NAME,OBSERVATION) %>%
   count()
Names_2check<-Names_2check%>% arrange(as.numeric(OBSERVATION))

Euring<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)%>%
  mutate(Code=as.numeric(Code))%>%
  select(Code,ENGLISH_NAME)%>%
  # update Arctic Tern Code
  mutate(Code=case_when(Code==6169~6159,TRUE ~ Code))

Names_3check<-Names_2check %>%
  mutate(Code=as.numeric(OBSERVATION))%>%
  left_join(Euring,by='Code')%>%
  rename(ENGLISH_NAME_provided=ENGLISH_NAME.x,
         ENGLISH_NAME_expected=ENGLISH_NAME.y)%>%
  mutate(check=(ENGLISH_NAME_provided==ENGLISH_NAME_expected))%>%
  relocate(Code,OBSERVATION,ENGLISH_NAME_expected, ENGLISH_NAME_provided,n)%>%
  rename('Code provided'=OBSERVATION,
         'Code expected'=Code,
         'Name provided'=ENGLISH_NAME_provided,
         'Name expected'=ENGLISH_NAME_expected,
         'Name fitting'=check)

Names_4check<-Names_3check %>%
  select('Code provided','Name provided','Name fitting',n)

Species_Table<- flextable(Names_4check)
Species_Table <- set_table_properties(Species_Table, width = 1, layout = "autofit")
Species_Table
```


These species will not be included in the map.

```{r CodesInternalCheck, echo=FALSE}
# Check names not fitting
if (nrow(filter(Names_3check, `Name fitting` == FALSE)) == 0) {
  cat("There are no missing names")
} else {
    cat("Please correct the following names")
  knitr::kable(
  Names_3check %>%
    filter(`Name fitting` == FALSE)%>%
  select('Code provided','Code expected','Name provided','Name expected','Name fitting',n)
  )
}
```

```{r CodesTax, echo=FALSE}
Euring_Tax<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)%>%
  mutate(Code=as.numeric(Code))%>%
  select(Code,ENGLISH_NAME,Artificial_tax_class)%>%
  # update Arctic Tern Code
  mutate(Code=case_when(Code==6169~6159,TRUE ~ Code))

Names_4tax<- subset(Names_1check, OBSERVATION != "0")
Names_5tax<-left_join(Names_4tax,Euring_Tax,by='ENGLISH_NAME')
Names_6taxmissing<-Names_5tax %>% 
  filter(is.na(Artificial_tax_class))

Names_7taxmissing<-Names_6taxmissing %>% 
  group_by(ENGLISH_NAME,Artificial_tax_class)%>% 
  tally()

# Check names not fitting
if (length(unique(Names_7taxmissing$ENGLISH_NAME)) == 0) {
  cat("There are no species missing tax/morphological classification.")
} else {
  cat("These species are missing tax/morphological classification.")
  knitr::kable(Names_7taxmissing)
}
```

\newpage

# Match mismatch

The selection of images for inspection should be random. The persons in the screening and ID control roles should not know whether they are determining a sighting (or during screening) or checking the determination (blind control). 

At the ID control level, care must be taken to ensure that the controls include as many species and taxonomic groups as possible.  

```{r AuditedObservationPlot, echo=F, fig.width=10, fig.height=4.5, warning=FALSE}
# Replace zeros
Audited_1check<-Plausability_Observations%>%
  mutate(ID_MATCH_MISMATCH = replace_na(ID_MATCH_MISMATCH, "0"))

ggplot(data=Audited_1check,aes(x=OBSERVATION_ID,y=as.numeric(ID_MATCH_MISMATCH)))+
    geom_point(aes(colour = factor(ID_MATCH_MISMATCH)), size = 1) +
    xlab("Observation_ID")+ylab('Match Mismatch')+
  theme_classic()+ 
  theme(axis.title = element_text(size=15),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size=15),
        legend.position='none')+
  scale_y_continuous(limits=c(-0.5,2.5))+ 
  scale_color_manual(values=c("0"="black",
                              "1"="#457b9d",
                              "2"="#e63946"))+
  NULL
```

Shows the proportion of animal identification that were matched the initial identification.

```{r CheckMismatch, echo=FALSE}
if ("2" %in% Plausability_Observations$ID_MATCH_MISMATCH==FALSE){
    print("Missing 2 in ID_MATCH_MISMATCH, errors in identification can not be calculated")
  }else{
Table_Identification<-Observations %>%
  group_by(ID_MATCH_MISMATCH)%>%
  tally()%>%
  pivot_wider(names_from=ID_MATCH_MISMATCH, values_from=n)%>%
  rename(Match=1,
         Mismatch=2,
         Unchecked=3)%>%
  mutate(Prop_checked=(Match+Mismatch)*100/(Unchecked+Match+Mismatch))%>%
  mutate(Prop_checked=round(Prop_checked,2))%>%
  mutate(Proportion_matched=(Match*100)/(Match+Mismatch))%>%
  mutate(Proportion_matched=round(Proportion_matched,2))
names(Table_Identification)<-c('Match','Mismatch','Not Audited','Audited [%]','Matched [%]')
Table_Identification<- flextable(Table_Identification)
# Set column widths manually (in inches)
Table_Identification<- set_table_properties(Table_Identification, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   # column 1 = 2 inches
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2) 
# Print table 
Table_Identification}
```

## Mismatch

How many animals were first **misidentified**?

```{r, echo=FALSE}
if ("2" %in% Audited_1check$ID_MATCH_MISMATCH==FALSE){
    print("Missing 2 in ID_MATCH_MISMATCH, errors in identification can not be calculated")
  }else{
Audited_2check<-Audited_1check %>%
  group_by(ENGLISH_NAME,ID_MATCH_MISMATCH)%>%
  tally()%>%
  pivot_wider(names_from=ID_MATCH_MISMATCH, values_from=n)

Audited_3check<-Audited_2check%>%
  rename(ID_match="1",
         ID_mismatch="2",
         Not_checked="0")

Audited_4check<-Audited_3check %>%
  filter(ID_match!=0 & ID_mismatch != 0) 
  
Audited_5check<-Audited_4check %>% select(ENGLISH_NAME,ID_match,ID_mismatch)

Table_biases <- flextable(Audited_5check)
# Set column widths manually (in inches)
Table_biases<- set_table_properties(Table_biases, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   # column 1 = 2 inches
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2) 
# Print table 
Table_biases
}
```

\newpage

## Biases

Are there any species that require revision due to frequent misidentification? If so, consider conducting a reevaluation. For example, that the errors were more frequent than the matches. 

```{r, echo=FALSE}
if ("2" %in% Audited_1check$ID_MATCH_MISMATCH==FALSE){
    print("Missing 2 in ID_MATCH_MISMATCH, biases can not be calculated")
  }else{
Audited_7check<-Audited_5check %>%
  mutate(Commonly_mistaken=ID_mismatch>ID_match)%>%
  filter(Commonly_mistaken==TRUE)%>%
  select(ENGLISH_NAME,ID_match,ID_mismatch)
Audited_7check<- flextable(Audited_7check)
Audited_7check<- set_table_properties(Audited_7check, width = 1, layout = "autofit") 
Audited_7check}
```


Ensure that there is no observer bias, such as when a large number of individuals from one species are consistently misidentified.

```{r MissMatchPlot, echo=F,fig.width=10, fig.height=10}
if ("2" %in% Audited_1check$ID_MATCH_MISMATCH==FALSE){
    print("Missing 2 in ID_MATCH_MISMATCH, plot can not be created")
  }else{
  Audited_6check<-Audited_5check %>% 
    pivot_longer(cols = c("ID_match","ID_mismatch"),names_to = "TYPE")
  
  ggplot(data=Audited_6check, aes(x=ENGLISH_NAME, y=value, fill=TYPE)) +
      geom_bar(stat="identity", position=position_dodge())+
      ylab('Controlled sightings')+
      xlab('')+
      coord_flip()+
      scale_y_continuous(expand = c(0,0),
                         limits=c(0,max(Audited_6check$value)+
                                    mean(Audited_6check$value)))+
  scale_fill_manual(values=c('#999999','#E69F00'))+
  theme_classic()+
  theme(axis.title = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=10),
        legend.position='top')
}
```



\newpage

# Detection Step

Gives insights on the proportion of missed animals during the screening process.

By definition 0 = No screening control, 1 = Only on screening, 2 = Only on control, 3 = Screening and Control (Agreement), 4 = Detected in ID, 5 = Detected in ID control.

```{r TableDetectionDefinitions, echo=FALSE}
Screening_1check<-Plausability_Observations %>%
    mutate(SCREENING=case_when(DETECTION_STEP == 1 ~ 'DETECTED_1SCREENING',
                               DETECTION_STEP == 2 ~ 'DETECTED_2CONTROL',
                               DETECTION_STEP == 3 ~ 'DETECTED_3AGREEMENT',
                               DETECTION_STEP == 4 ~ 'DETECTED_4ID',
                               DETECTION_STEP == 5 ~ 'DETECTED_5ID_CONTROL',
                               DETECTION_STEP == 0 ~ 'NO_SCREENING_CONTROL',
                               TRUE  ~ 'NOT_CHECKED'))

Screening_2check<-Screening_1check %>%
  group_by(SCREENING)%>%
  tally()

Screening_3check<-Screening_2check %>%
  pivot_wider(names_from=SCREENING, values_from=n) 
```

```{r Detection_Table, echo=FALSE}
Detection_Table<-Screening_3check %>%
  mutate(Proportion_reviewed=(DETECTED_1SCREENING+DETECTED_2CONTROL+DETECTED_3AGREEMENT)*100/
           (DETECTED_1SCREENING+DETECTED_2CONTROL+DETECTED_3AGREEMENT+NOT_CHECKED))%>%
  mutate(Proportion_reviewed=round(Proportion_reviewed,2))%>%
  mutate(Proportion_agreement=(DETECTED_3AGREEMENT)*100/
           (DETECTED_1SCREENING+DETECTED_2CONTROL+DETECTED_3AGREEMENT))%>%
  mutate(Proportion_agreement=round(Proportion_agreement,2))%>%
  rename('Screener'=DETECTED_1SCREENING,
         'Reviewer'=DETECTED_2CONTROL,
         'Agreement'=DETECTED_3AGREEMENT,
         'Not Reviewed'=NOT_CHECKED,
         'Reviewed [%]'=Proportion_reviewed,
         'Agreement [%]'=Proportion_agreement
  )
Table_Detection<- flextable(Detection_Table)
# Set column widths manually (in inches)
Table_Detection<- set_table_properties(Table_Detection, width = 1, layout = "autofit") 
# Print table 
Table_Detection
```


### Formula

Using the Lincoln-Petersen mark-recapture formula N= MC/R, we estimated the total number of animals encountered during the survey. In this formula, M represents the total number of animals found by the screener, C is the total number of animals found by the auditor, and R is the number of animals detected by both the screener and the auditor. The value of N represents the estimated number of animals findable in the pictures.  
Based on these results, the efficiency of the screener was calculated as s = M/N, and the efficiency of the auditor as a = C/N.  
Since the screener and the auditor are assigned randomly and therefore interchangeable, the overall efficiency of a single person reviewing the footage, referred to as single control efficiency was calculated as sc = (s+a)/2. 
Assuming 20% of the area audited, the efficiency for this 20% is defined as db = (M+C-R)/N. If the efficiency of the entire process is to be calculated then rl = (dc*0.2)+(sc*0.8).  However, the actual number of animals remains unknown and therefore the number of missed animals is underestimated . 

```{r TableFormulaDetection, echo=FALSE}
FormulaDetection_Table<-Detection_Table %>%
  dplyr::select(Screener,Reviewer,Agreement)%>%
  rename(m=Screener,
         c=Reviewer,
         o=Agreement)%>%
  mutate(
         M=m+o,
         C=c+o,
         R=o,
         N=(M*C)/R,
         s=M/N,
         a=C/N,
         sc=(s+a)/2,
         dc=(M+C-R)/N,
         rl=(dc*0.2)+(sc*0.8))%>%
  mutate(N=round(N,2),
         s=round(s,2),
         a=round(a,2),
         sc=round(sc,2),
         dc=round(dc,2),
         rl=round(rl,2))%>%
  dplyr::select(M,C,R,N,s,a,sc,dc,rl)
```

```{r TableFormulaDetectionKnitr, echo=FALSE}
Table_FormulaDetection <- flextable(FormulaDetection_Table)
# Set column widths manually (in inches)
Table_FormulaDetection<- set_table_properties(Table_FormulaDetection, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   # column 1 = 2 inches
  width(j = 2, width = 1.5) %>% # column 2 = 1.5 inches
  width(j = 3, width = 1.2)     # etc.
# Print table 
Table_FormulaDetection
```


\newpage

# Proportion animals

How many **marine mammals** and **birds** were sighted?

```{r Taxa, echo=FALSE}
Animals_1check<-Names_5tax %>%
  mutate(Taxa=case_when(Artificial_tax_class == 'Marine_mammals' ~ "Mammals",
                        TRUE ~ "Birds"))
```

```{r TaxaPlot, echo=FALSE, fig.width=5, fig.height=4}
#Check proportion marine mammals and birds
Animals_2check<-Animals_1check %>% group_by(Taxa) %>% tally()
ggplot(Animals_2check, aes(x=Taxa, y=n, fill=Taxa))+
  geom_bar(stat='identity')+
  theme(legend.position = 'none')+
  xlab('Taxa')+ylab('Number of sightings')+
  theme_classic()+ 
  scale_y_continuous(expand = c(0,0)) +
  theme(axis.title = element_text(size=15),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15),
        legend.position='none')+
  scale_fill_manual(values=c("#2a9d8f","#264653"))
```

### Most common birds per survey

```{r CommonBirdsPlot, echo=F, fig.width=12, fig.height=4}
#Calculate number of observations per species
Birds_1check<-Animals_1check %>% filter(Taxa=='Birds')
Birds_2check<-Birds_1check %>% 
  group_by(ENGLISH_NAME,OBSERVATION,Taxa) %>%
  count()
Birds_3check<-Birds_2check %>%
  arrange(desc((n)))%>%
  head(5)
ggplot(Birds_3check, aes(x=ENGLISH_NAME, 
                         y=n, 
                         fill=ENGLISH_NAME,
                         order = -as.numeric(n))) +
  geom_bar(stat='identity',position = position_dodge())+
  ylab("Sightings")+xlab("")+
  theme_classic()+ 
  coord_flip()+ 
  scale_y_continuous(expand = c(0,0),
                     limits=c(-0.5,max(Birds_3check$n)+mean(Birds_3check$n)))+
  theme(axis.title =  element_text(size=20),
        axis.text.x = element_text(size=20, angle=45,hjust=1),
        axis.text.y = element_text(size=20),
        legend.position='none')+
  scale_fill_manual(values=c("#5f0f40","#9a031e","#fb8b24","#e36414",
                             "#0f4c5c","#05668d","#d9ed92","#ff9f1c",
                             "#e71d36","#2ec4b6","#43aa8b","#277da1"))
```

### All bird sighthings

```{r BirdsSightingsPlot, echo=FALSE, fig.height=10, fig.width=8}
Birds_4check<-Animals_1check %>% filter(Taxa=='Birds')
Birds_5check<-Birds_4check %>% 
  group_by(ENGLISH_NAME,OBSERVATION,Artificial_tax_class) %>%
  count()
ggplot(Birds_5check, aes(x=paste(str_pad(OBSERVATION, 6, pad = "0"),
                                 ENGLISH_NAME), 
                         y=n,
                         fill=Artificial_tax_class)) +
  geom_bar(stat='identity')+
  coord_flip() +
  ylab("Sightings")+xlab("Species")+
  scale_y_continuous(expand = c(0,0),
                     limits=c(-0.5,max(Birds_5check$n)+mean(Birds_5check$n)))+
  theme_classic()+ 
  theme(axis.title = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=10),
        legend.position='none')+
  scale_fill_manual(values=c("#5f0f40","#9a031e","#fb8b24","#e36414",
                             "#0f4c5c","#05668d","#5f0f40","#9a031e",
                             "#fb8b24","#e36414","#0f4c5c","#05668d"))
```


\newpage

# Plausability

## Activity 

Shows the proportion of activities recorded in all animals.  
Only swimming and flying considered for the calculation.  
It is expected that the proportion of swimming animals is higher than that of flying. 

```{r TableActivity, echo=FALSE}
Table_Activity<-Plausability_Observations %>%
  drop_na(OBSERVATION)%>%
  group_by(ACTIVITY)%>%
  tally()%>%
  pivot_wider(names_from=ACTIVITY, values_from=n)%>%
  # Fill missing activity columns with 0
  mutate(
    `3` = if (!"3" %in% names(.)) 0 else `3`,
    `4` = if (!"4" %in% names(.)) 0 else `4`,
    `5` = if (!"5" %in% names(.)) 0 else `5`,
    `NA` = if (!"NA" %in% names(.)) NA else `NA`
  )%>%
  rename(Swimming="1",
         Flying="2",
         Submerged="3",
         Breaching_surface="4",
         Associated_with_platform="5",
         Undeclared="NA")%>%
  mutate(Prop_flying=(Flying*100)/(Flying+Swimming))%>%
  mutate(Prop_flying=round(Prop_flying,2))%>%
  mutate(Prop_swimming=round(100-Prop_flying,2))%>%
  select(Prop_swimming,Prop_flying,Swimming,Flying)%>%
  rename('Swimming'=Swimming,
         'Flying'=Flying,
         'Flying [%]'=Prop_flying,
         'Swimming [%]'=Prop_swimming)
Table_Activity <- flextable(Table_Activity)
# Set column widths manually (in inches)
Table_Activity<- set_table_properties(Table_Activity, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2.5) 
Table_Activity
```

Expected that birds are flying or swimming. Marine mammals swimming or porpoising. Undeclared for animals is not allowed. 

```{r ActivityTable,echo=FALSE}
Activity_Table<-Observations %>%
  group_by(ENGLISH_NAME,ACTIVITY)%>%
  tally()%>%
  pivot_wider(names_from=ACTIVITY,values_from=n)
Activity_Table<-Activity_Table %>%
   mutate(
    `3` = if (!"3" %in% names(.)) 0 else `3`,
    `4` = if (!"4" %in% names(.)) 0 else `4`,
    `5` = if (!"5" %in% names(.)) 0 else `5`,
    `0` = if (!"0" %in% names(.)) NA else `0`
  )%>%
  rename(Swimming="1",
         Flying="2",
         Submerged="3",
         Breaching_surface="4",
         Associated_with_platform="5",
         Undeclared="0")%>%
  mutate(Swimming = replace_na(Swimming, 0),
         Flying= replace_na(Flying, 0),
         Submerged= replace_na(Submerged, 0),
         Breaching_surface= replace_na(Breaching_surface, 0),
         Associated_with_platform= replace_na(Associated_with_platform, 0),
         Undeclared= replace_na(Undeclared, 0)
         )%>%
  relocate(ENGLISH_NAME,Swimming,Flying,Submerged,Breaching_surface,Associated_with_platform)%>%
  rename('Swimming'=Swimming,
         'Flying'=Flying,
         'Submerged'=Submerged,
         'Breaching'=Breaching_surface,
         'Association'=Associated_with_platform)
Activity_Table <- flextable(Activity_Table)
# Set column widths manually (in inches)
Activity_Table<- set_table_properties(Activity_Table, width = 1, layout = "autofit") %>%
  width(j = 1, width = 2) %>%   
  width(j = 2, width = 2) %>% 
  width(j = 3, width = 2.5) 
Activity_Table
```



\newpage

## Age class

AGE_CLASS: Expected A- Adult, IM- Immature; AGE_YEARS: Expected numeric from 1 to 5. 

```{r CheckAge,echo=FALSE}
if ("IM" %in% Observations$AGE_CLASS==FALSE){
  print("No table would be created as there is no IM information in the column AGE_CLASS")
  }else{
Age_table <- Observations %>%
  drop_na(AGE_CLASS) %>%
  group_by(ENGLISH_NAME, AGE_CLASS, AGE_YEARS) %>%
  tally() %>%
  pivot_wider(names_from = AGE_CLASS, values_from = n) %>%
  select(ENGLISH_NAME, A, IM, AGE_YEARS)
Age_table <- Age_table %>%
  pivot_wider(
    names_from = AGE_YEARS,
    values_from = IM,
    names_prefix = "IM_"
  ) %>%
  rename_with(~gsub("IM_NA", "Undeclared", .x)) %>%
  group_by(ENGLISH_NAME) %>%
  summarise(across(everything(), ~sum(.x, na.rm = TRUE))) %>%
  relocate(ENGLISH_NAME, starts_with("IM_"), A, Undeclared)
Age_table <- flextable(Age_table)
# Set column widths manually (in inches)
Age_table<- set_table_properties(Age_table, width = 1, layout = "autofit") 
Age_table
}
```

## Sex

F for Females and M for Males. 
Only retains species where this information was provided.

```{r CheckSex,echo=FALSE}
if (!any(c("F", "M") %in% Observations$SEX)) {
  print("No table would be created as there is no F or M information in the column SEX")
  }else{
  Table_Sex<-Observations %>%
    group_by(ENGLISH_NAME,SEX)%>%
    tally()%>%
    pivot_wider(names_from = SEX,values_from=n)%>%
    drop_na(F)%>%
    select(ENGLISH_NAME,F,M)
  Table_Sex
Table_Sex <- flextable(Table_Sex)
# Set column widths manually (in inches)
Table_Sex<- set_table_properties(Table_Sex, width = 1, layout = "autofit") 
Table_Sex
} 
```


\newpage

# Spatial distributions per morphological group

All observation will be plotted by taxonomic/morphological group. **If you can not see all species is likely that is because they are overlapping, please refer to the dynamic maps to see the location of each species.** Dynamic maps are under the folder 03Maps. The name of the files correspond to the survey. There you can zoom in and out and click on the dots to get information on the species sighted. 

```{r SpatialPlotAxis,echo=FALSE}
y_start<-min(as.numeric(Plausability_Basis$LAT_PIC_CENTER), na.rm = TRUE)-0.5
y_end<-max(as.numeric(Plausability_Basis$LAT_PIC_CENTER), na.rm = TRUE)+0.5
x_start<-min(as.numeric(Plausability_Basis$LON_PIC_CENTER), na.rm = TRUE)-1
x_end<-max(as.numeric(Plausability_Basis$LON_PIC_CENTER), na.rm = TRUE)+1
```

```{r SpatialPlotFunction, echo=FALSE}
CheckGroup <- function(Group) {
  SelectedBirds <- subset(Animals_1check, Artificial_tax_class == Group)
  
  if(nrow(SelectedBirds) == 0) {
        print(paste("No",Group,"occurred in the survey, therefore there is nothing to be plotted"))
   } else {
          
  SelectedBirds$lat<-as.numeric(SelectedBirds$LAT_OBJECT)
  SelectedBirds$lon<-as.numeric(SelectedBirds$LON_OBJECT)
  
  SelectedBirds <- SelectedBirds[!is.na(SelectedBirds$lat) & !is.na(SelectedBirds$lon), ]
  SelectedBirds_sf <- st_as_sf(SelectedBirds, coords = c("lon", "lat"),crs = 4326, agr = "constant")
  
  ggplot(data = SelectedBirds_sf) +
    geom_sf(data = Study_areas,colour = 'black', alpha=0.1)+
    geom_sf(data = Land, colour = 'black', fill = '#e5e5e5')+
    
    geom_point(data=SelectedBirds,aes(x=lon, y= lat, fill = ENGLISH_NAME), 
             size=3, shape=21,color='black') +
    
    scale_fill_manual(values= c(
      "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd",
      "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf",
      "#393b79", "#637939", "#8c6d31", "#843c39", "#7b4173",
      "#3182bd", "#31a354", "#756bb1", "#636363", "#e6550d",
      "#fd8d3c", "#fdae6b", "#fdd0a2", "#9ecae1", "#6baed6",
      "#4292c6", "#2171b5", "#08519c", "#08306b", "#c7e9c0",
      "#fa9fb5", "#a1d99b"
))+
    theme_bw()+
    xlab('Longitude')+ylab('Latitude')+
    theme(legend.text=element_text(size=20),
          axis.text = element_text(size=20),
          axis.title = element_blank())+
    coord_sf(xlim = c(x_start, x_end), ylim = c(y_start, y_end), expand = FALSE)+
    scale_x_continuous(labels = function(x) paste0(x, '\u00B0', "W")) +
    scale_y_continuous(labels = function(x) paste0(x, '\u00B0', "N"))}
}

```

### Gulls

Species occurring in the survey

```{r GullsMap, echo=FALSE, comment=NA,fig.width=14, fig.height=10}
CheckGroup(Group="Gulls")
```

\newpage

### Skuas
Species occurring in the survey

```{r SkuasMap, echo=F, comment=NA, fig.width=14, fig.height=10}
CheckGroup(Group="Skuas")
```

\newpage

### Gannets and Cormorants
Species of occurring in the survey

```{r GannetMap, echo=FALSE, eval=TRUE, fig.width=14, fig.height=10}
CheckGroup(Group="Gannets_Cormorants")
```

\newpage

### Auks
Species  occurring in the survey

```{r AuksMap, echo=FALSE,comment=NA, fig.width=14, fig.height=10}
CheckGroup(Group='Auks')
```

\newpage

### Terns

Species occurring in the survey

```{r TernsMap, echo=FALSE, comment=NA,fig.width=14, fig.height=10}
CheckGroup(Group='Terns')
```
\newpage

### Ducks and Shelducks

Species of occurring in the survey

```{r AnatidaeMap, echo=FALSE,comment=NA, fig.width=14, fig.height=10}
CheckGroup(Group="Ducks_Shelducks")
```

\newpage

### Geese and Swans
Species occurring in the survey

```{r GesseMap, echo=FALSE, eval=TRUE, fig.width=14, fig.height=10, comment=NA}
CheckGroup(Group="Swan_Geese")
```

\newpage

### Divers
Species occurring in the survey

```{r DiverMap, echo=FALSE, eval=TRUE, fig.width=14, fig.height=10, comment=NA}
CheckGroup(Group='Divers')
```

\newpage

### Grebes
Species occurring in the survey

```{r GrebesMap, echo=FALSE, comment=NA,fig.width=14, fig.height=10}
CheckGroup(Group='Grebes')
```

\newpage

### Waders
Species occurring in the survey

```{r WadersMap, echo=FALSE, comment=NA,fig.width=14, fig.height=10}
CheckGroup(Group='Waders')
```

\newpage

### Marine mammals
Species occurring in the survey

```{r MammalsMap, echo=FALSE,comment=NA, fig.width=14, fig.height=10}
CheckGroup(Group='Marine_mammals')
```

\newpage

### Other seabird species
Species occurring in the survey

```{r SeabirdsMap, comment=NA,echo=FALSE, fig.width=14, fig.height=10}
CheckGroup(Group='Other_seabirds')
```

\newpage

### Other bird species
Species occurring in the survey

```{r OthersMap, comment=NA,echo=FALSE, fig.width=14, fig.height=10}
CheckGroup(Group='Other_species')
```



 ***End of the document. ***