---
title: "Separated Maps"
author: "Seabird Monitoring"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  ThisDirectory: ThisDirectory
  ThisFile: ThisFile
  Survey_BasisDaten: Maps_BasisDaten
  Survey_Observations: Maps_Observations
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fontawesome)
```

# Intro

Using data from **`r params$ThisFile`** excel file.  
This document presents two maps:

- The first map shows the Survey Observations and base positions.

- The second map displays the sightings.

Please note that rendering may take some time due to the large number of points. Thank you for your patience.  ⏳

```{r Packages, echo=FALSE, warnings=FALSE}
library(sf)
library(tmap)
library(ggplot2)
library(tidyverse)
```

```{r LoadShapefiles, echo=FALSE, include=FALSE, eval=TRUE}
Study_areas<-GermanNorthSea::Study_areas
Protected_SCA<- GermanNorthSea::German_SCA
Alemania<- GermanNorthSea::German_land
Protected_natura <- GermanNorthSea::German_natura
WindFarms<- GermanNorthSea::OWF_EMODnet
```

## Position accuracy

Basis position and Observations positions are plotted on the map.<br> 

Once the map has loaded, temporary **unselect** the layer BP (Basis Points).<br>  
Then, zoom into your area of interest using the blue dots as a reference.<br> 
After zooming, re-enable the BP layer.<br> 
This saves rendering time.<br> 

Points shown in  <span style="color: #ff595e;">red</span> represent data from **Basis**, based on their longitude and latitude.<br>
Points shown in <span style="color: #1982c4;"> blue</span>represent data from **Observations**, based on their longitude and latitude. <br> 

You can interact with the map using the following controls:<br> 
Using `r fa("plus", fill = 'black')` **zoom-in** to examine points in detail.<br> 
Using `r fa("minus", fill = 'black')` **zoom-out** for a broader view.<br>  
Using `r fa("layer-group", fill = 'black')` toogle **layers** on and off.<br>  
Hover over a blue dot with the cursor `r fa("mouse-pointer", fill = 'black')` When the icon changes to `r fa("hand-point-up", fill = 'black')`, click it to view the position ID and species information.<br> 


```{r AccuracyBase, include=FALSE, echo=FALSE, eval=TRUE}
BasisPos<-params$Survey_BasisDaten
ObsPos<-params$Survey_Observations
```

```{r substitute, echo=FALSE, eval=FALSE}
BasisPos<-Maps_BasisDaten
ObsPos<-Maps_Observations
```

```{r BasisFortify, echo=FALSE}
BasisPosition<-fortify(BasisPos)
BasisPosition<-as.data.frame(BasisPosition) #ADDED 13-04-2021
BasisPosition$lat<-as.numeric(BasisPosition$LAT_PIC_CENTER)
BasisPosition$lon<-as.numeric(BasisPosition$LON_PIC_CENTER)
BasisPosition <- BasisPosition[!is.na(BasisPosition$lat), ] #Eliminar NAs
BasisPositionC <- st_as_sf(BasisPosition, coords = c("lon", "lat"),crs = 4326, agr = "constant")
```

```{r ObsFortify, include=FALSE, echo=FALSE, warnings=FALSE, eval=TRUE}
ObsPos$OBSERVATION_ID<-ObsPos$Observation_ID
ObservedPositionDots<-fortify(ObsPos)
ObservedPositionDots<-as.data.frame(ObservedPositionDots)
ObservedPositionDots$lat<-ObservedPositionDots$LAT_OBJECT
ObservedPositionDots$lon<-ObservedPositionDots$LON_OBJECT
ObservedPositionC <- ObservedPositionDots
ObservedPositionC <- ObservedPositionC[!is.na(ObservedPositionC$lat), ] #Eliminar NAs
ObservedPositionC<- st_as_sf(ObservedPositionC, coords = c("lon", "lat"), crs = 4326)
```

```{r SubsetColumns, echo=FALSE, eval=FALSE}
BasisPositionC<-BasisPositionC[,c("POSITION_ID","CAMERA_NUMBER")]
ObservedPositionC<-ObservedPositionC[,c("OBSERVATION_ID","ENGLISH_NAME")]
```

```{r StaticMap, include=FALSE, echo=FALSE, warnings=FALSE, eval=TRUE}
PlotSurvey<-tm_shape(BasisPositionC) + 
  tm_dots(id = "CRUISENO",
          col="red",
          popup.vars=c("Position_ID"="POSITION_ID","Camera"="CAMERA_NUMBER"))+
  tm_shape(ObservedPositionC) + 
  tm_dots(id = "CRUISENO",
          col="blue",
          popup.vars=c("Observation_ID"="OBSERVATION_ID","Specie"="ENGLISH_NAME"))+
  tm_layout(legend.bg.color = 'white',  #Fondo de la etiqueta
            legend.position = c(0.1,"bottom"),  #Position de la etiqueta
            legend.frame = TRUE) #Frame de la etiqueta
```

```{r Vista, echo=FALSE, include=FALSE, eval=TRUE}
tmap_mode("view") #interactive tmap_mode("view")
```

```{r PlotSurveyDynamic, echo=FALSE, include=TRUE, warning=FALSE, message=FALSE, eval=TRUE}
PlotSurvey
```

## Sightings

This map contains all the **sightings** separated by taxonomic group.  
Each taxonomic groups is separated by **color**  

Ducks and Shelducks in <span style="color: #ffca3a;">yellow</span>; 
Swans and Geese in <span style="color: #c5ca30;">green-yellow</span>; 
Divers in <span style="color: #ff595e;">red</span>; 
Grebes in <span style="color: #1982c4;">light blue</span>; 
Gannets and cormorants <span style="color: #ff924c;">orange</span>; 
Auks in <span style="color: #36949d;">grey blue</span>; 
Gulls in <span style="color: #565aa0;">light purple</span>; 
Skuas in <span style="color: #8ac926;">green</span>; 
Terns in <span style="color: #6a4c93;">purple</span>; 
Waders in <span style="color: #4267ac;">darkblue</span>; 
Other seabirds and other species in  <span style="color: #333533;">grey</span>; 
Marine mammals in  <span style="color: #202020;">black</span>.


```{r Separate groups, include=FALSE, echo=FALSE, warnings=FALSE}
Euring<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)
ObservedPositionC_1<-subset(ObservedPositionC, ObservedPositionC$ENGLISH_NAME != "0")
ObservedPositionC_2<-merge(ObservedPositionC_1,Euring,by='ENGLISH_NAME')
ObservedPositionC_2<-ObservedPositionC_2 %>%
  rename(TaxGroups=Artificial_tax_class)
```

```{r CheckGroups, include=FALSE, echo=FALSE}
ObservedPositionC_3group<-ObservedPositionC_2 %>%
  group_by(TaxGroups) %>%
  count(TaxGroups)
```

```{r BaseMap,echo=FALSE}
BaseMap<- tm_shape(Study_areas)+  #Grid de Study_areas
  tm_polygons(col='#74c69d')+
  tm_shape(Protected_SCA)+  #Area protegida Este
  tm_polygons(col='#40916c')+
  tm_shape(Protected_natura)+  #Area protegida Oeste
  tm_polygons(col='#40916c')+ 
  tm_shape(WindFarms)+  #WindFarms
  tm_polygons(col='#9d0208')
```

```{r BaseMapDinamic,echo=FALSE, eval=FALSE}
tmap_mode("view") 
BaseMap
```

```{r AddGulls, echo=FALSE}
SeparateGulls<-function(TaxonomicGroup=TaxonomicGroup){
  GullsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(GullsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         print(paste(TaxonomicGroup,"will be included in the map"))
        BaseMap<-BaseMap+
           tm_shape(GullsSub) + 
             tm_dots(id = "TaxGroups",
                       col="#565aa0",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignGulls, echo=FALSE, comment=NA}
SeparateGulls(TaxonomicGroup='Gulls')
```

```{r AddSkuas, echo=FALSE}
SeparateSkuas<-function(TaxonomicGroup=TaxonomicGroup){
  SkuasSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(SkuasSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         print(paste(TaxonomicGroup,"will be included in the map"))
          BaseMap<-BaseMap+
           tm_shape(SkuasSub) + 
            tm_dots(id = "TaxGroups",
              col="#8ac926",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignSkuas, echo=FALSE, comment=NA}
SeparateSkuas(TaxonomicGroup="Skuas")
```

```{r AddGannets, echo=FALSE}
SeparateGannets<-function(TaxonomicGroup=TaxonomicGroup){
  GannetsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(GannetsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
          print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(GannetsSub) + 
             tm_dots(id = "TaxGroups",
                       col="#ff924c",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignGannets, echo=FALSE, comment=NA}
SeparateGannets(TaxonomicGroup='Gannets_Cormorants')
```

```{r AddAuks, echo=FALSE}
SeparateAuks<-function(TaxonomicGroup=TaxonomicGroup){
  AuksSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(AuksSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(AuksSub) + 
            tm_dots(id = "TaxGroups",
              col="#36949d",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
    assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignAuks, echo=FALSE, comment=NA}
SeparateAuks(TaxonomicGroup="Auks")
```

```{r AddTerns, echo=FALSE}
SeparateTerns<-function(TaxonomicGroup=TaxonomicGroup){
  TernsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(TernsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
          print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(TernsSub) + 
            tm_dots(id = "TaxGroups",
                     col="#6a4c93",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignTerns, echo=FALSE, comment=NA}
SeparateTerns(TaxonomicGroup='Terns')
```

```{r AddDucks, echo=FALSE}
SeparateDucksShelducks<-function(TaxonomicGroup=TaxonomicGroup){
  DucksShelducksSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(DucksShelducksSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
           print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(DucksShelducksSub) + 
            tm_dots(id = "TaxGroups",
                     col="#ffca3a",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
         #substitutes base map adding the layer
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignDucks,  echo=FALSE, comment=NA}
SeparateDucksShelducks(TaxonomicGroup="Ducks_Shelducks")
```

```{r AddGeeseSwan,echo=FALSE}
SeparateSwanGeese<-function(TaxonomicGroup=TaxonomicGroup){
 SwanGeeseSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(SwanGeeseSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
           print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(SwanGeeseSub) + 
            tm_dots(id = "TaxGroups",
                     col="#c5ca30",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignGesseSwan,  echo=FALSE, comment=NA}
SeparateSwanGeese(TaxonomicGroup="Swan_Geese")
```

```{r AddDivers, echo=FALSE}
SeparateDivers<-function(TaxonomicGroup=TaxonomicGroup){
 DiversSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(DiversSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
           print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(DiversSub) + 
            tm_dots(id = "TaxGroups",
                     col="#ff595e",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignDivers, echo=FALSE, comment=NA}
SeparateDivers(TaxonomicGroup='Divers')
```

```{r AddGrebes, echo=FALSE}
SeparateGrebes<-function(TaxonomicGroup=TaxonomicGroup){
  GrebesSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(GrebesSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
          print(paste(TaxonomicGroup,"will be included in the map"))
         BaseMap<-BaseMap+
           tm_shape(GrebesSub) + 
             tm_dots(id = "TaxGroups",
                       col="#1982c4",
                       popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignGrebes,  echo=FALSE, comment=NA}
SeparateGrebes(TaxonomicGroup='Grebes')
```

```{r AddWaders, echo=FALSE}
SeparateWaders<-function(TaxonomicGroup=TaxonomicGroup){
  WadersSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(WadersSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         BaseMap<-BaseMap+
           tm_shape(WadersSub) + 
             tm_dots(id = "TaxGroups",
                       col="#4267ac",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignWaders, echo=FALSE, comment=NA}
SeparateWaders(TaxonomicGroup='Waders')
```

```{r AddSeabirds, echo=FALSE}
SeparateSeabirds<-function(TaxonomicGroup=TaxonomicGroup){
  OtherSeabirdsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(OtherSeabirdsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         print(paste(TaxonomicGroup,"will be included in the map"))
          BaseMap<-BaseMap+
           tm_shape(OtherSeabirdsSub) + 
            tm_dots(id = "TaxGroups",
                     col="#333533",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
   assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssingSeabirds,  echo=FALSE, comment=NA}
SeparateSeabirds(TaxonomicGroup='Other_seabirds')
```

```{r AddOthers, echo=FALSE}
SeparateOthers<-function(TaxonomicGroup=TaxonomicGroup){
  OtherBirdsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(OtherBirdsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
         print(paste(TaxonomicGroup,"will be included in the map"))
          BaseMap<-BaseMap+
           tm_shape(OtherBirdsSub) + 
            tm_dots(id = "TaxGroups",
                     col="#333533",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignOthers,  echo=FALSE, comment=NA}
SeparateOthers(TaxonomicGroup='Other_species')
```

```{r AddMammals, echo=FALSE}
SeparateMarineMammals<-function(TaxonomicGroup=TaxonomicGroup){
 MarineMammalsSub<-subset(ObservedPositionC_2,ObservedPositionC_2$TaxGroups==TaxonomicGroup)
    if(nrow(MarineMammalsSub) == 0) {
        print(paste("No",TaxonomicGroup,"occurred in the survey"))
        } else {
          print(paste(TaxonomicGroup,"will be included in the map"))
          BaseMap<-BaseMap+
           tm_shape(MarineMammalsSub) + 
            tm_dots(id = "TaxGroups",
                     col="#202020",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BaseMap',BaseMap,envir=globalenv())}
  }
```

```{r AssignMarineMammals,  echo=FALSE, comment=NA}
SeparateMarineMammals(TaxonomicGroup="Marine_mammals")
```

You can interact with the map using the following controls:<br> 
Using `r fa("layer-group", fill = 'black')` to toogle **morphological** groups on and off.<br> 
Using `r fa("plus", fill = 'black')` to **zoom-in** and explore the points in more detail.<br>  
Using `r fa("minus", fill = 'black')` to **zoom-out** for a broader view.<br> 
Click on a point `r fa("mouse-pointer", fill = 'black')` to view the species information.<br> 

```{r BaseMapView, echo=FALSE, include=FALSE, eval=TRUE}
tmap_mode("view") #interactive tmap_mode("view")
```

```{r FinalMap, echo=FALSE, warnings=FALSE, message=FALSE, comment=FALSE}
BaseMap+
  tm_layout(legend.bg.color = 'white',
            legend.position = c(0.1,"bottom"), 
            legend.frame = TRUE) 
```



# End of document