---
title: "Separated Maps"
author: "Marine Vertebrate Monitoring"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  ThisDirectory: ThisDirectory
  ThisFile: ThisFile
  BasisDaten: BasisDaten
  Observations: Observations
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Intro

Using data from **`r params$ThisFile`** excel file.  
This document presents two maps:

- The first map shows the Survey Observations and base positions.

- The second map displays the sightings.

Please note that rendering may take some time due to the large number of points. Thank you for your patience.  ⏳

```{r Packages, echo=FALSE, warnings=FALSE}
library(sf)
library(tmap)
library(ggplot2)
library(tidyverse)
library(fontawesome)
```

## Position accuracy

Basis position and Observations positions are plotted on the map.<br> 

Once the map has loaded, temporary **unselect** the layer BP (Basis Points).<br>  
Then, zoom into your area of interest using the blue dots as a reference.<br> 
After zooming, re-enable the BP layer.<br> 
This saves rendering time.<br> 

Points shown in  <span style="color: #ff595e;">red</span> represent data from **Basis**, based on their longitude and latitude.<br>
Points shown in <span style="color: #1982c4;"> blue</span>represent data from **Observations**, based on their longitude and latitude. <br> 

You can interact with the map using the following controls:<br> 
Using `r fa("plus", fill = 'black')` **zoom-in** to examine points in detail.<br> 
Using `r fa("minus", fill = 'black')` **zoom-out** for a broader view.<br>  
Using `r fa("layer-group", fill = 'black')` toogle **layers** on and off.<br>  
Hover over a blue dot with the cursor `r fa("mouse-pointer", fill = 'black')` When the icon changes to `r fa("hand-point-up", fill = 'black')`, click it to view the position ID and species information.<br> 


```{r Parameters, include=FALSE, echo=FALSE, eval=TRUE}
Maps_BasisDaten<-params$BasisDaten
Maps_Observations<-params$Observations
```

```{r Manual, echo=FALSE, eval=FALSE}
Maps_BasisDaten<-BasisDaten
Maps_Observations<-Observations
```

```{r BasisLayer, echo=FALSE}
BasisDaten_df<-Maps_BasisDaten
BasisDaten_df$lat<-as.numeric(BasisDaten_df$LAT_PIC_CENTER)
BasisDaten_df$lon<-as.numeric(BasisDaten_df$LON_PIC_CENTER)
BasisDaten_df <- BasisDaten_df[!is.na(BasisDaten_df$lat) & !is.na(BasisDaten_df$lon), ] 
BasisDaten_sf <- st_as_sf(BasisDaten_df, coords = c("lon", "lat"),crs = 4326, agr = "constant")
```

```{r ObservationsLayer, echo=FALSE}
Observations_df<-Maps_Observations
Observations_df$lat<-as.numeric(Observations_df$LAT_OBJECT)
Observations_df$lon<-as.numeric(Observations_df$LON_OBJECT)
Observations_df <- Observations_df[!is.na(Observations_df$lat) & !is.na(Observations_df$lon), ] 
Observations_sf <- st_as_sf(Observations_df, coords = c("lon", "lat"),crs = 4326, agr = "constant")
```

```{r DisplayedInformation, echo=FALSE, eval=TRUE}
# check that columns exist
if (all(c("POSITION_ID", "CAMERA_NUMBER") %in% colnames(BasisDaten_sf))) {
  BasisDaten_positions<-BasisDaten_sf[,c("POSITION_ID","CAMERA_NUMBER")]
#check if position id exist
  } else {
  if ("POSITION_ID" %in% colnames(BasisDaten_positions) && any(!is.na(BasisDaten_positions$POSITION_ID))) {
  cat("POSITION_ID in BasisDaten exists and is not empty.\n")
} else {
  cat("POSITION_ID in BasisDaten is missing or empty.. Please check if there was a problem during the import to R.\n")
}
#check if camera number exists
  if ("CAMERA_NUMBER" %in% colnames(BasisDaten_positions) && any(!is.na(BasisDaten_positions$CAMERA_NUMBER))) {
  cat("CAMERA_NUMBER in BasisDaten exists and is not empty.\n")
} else {
  cat("CAMERA_NUMBER in BasisDaten is missing or empty. Please check if there was a problem during the import to R.\n")
}
}
```

```{r DisplayedInformationObservations, echo=FALSE, eval=TRUE}
#check that columns exist
if ("OBSERVATION_ID" %in% colnames(Observations_sf)){
  Observations_positions<-Observations_sf[,c("OBSERVATION_ID","ENGLISH_NAME")]
}else if ("Observation_ID" %in% colnames(Observations_sf)){
#rename if different name
Observations_sf <- Observations_sf %>%
  rename(OBSERVATION_ID = Observation_ID)
Observations_positions<-Observations_sf[,c("OBSERVATION_ID","ENGLISH_NAME")]
} else {
#if column doesnt exist show error
  cat("A column named Observation_ID or OBSERVATION_ID is missing. Please include")
}
```

```{r View, echo=FALSE, include=FALSE, eval=TRUE}
tmap_mode("view") #interactive tmap_mode("view")
```

```{r BasisMap, echo=FALSE, include=TRUE, warning=FALSE, message=FALSE, eval=TRUE}
tm_shape(BasisDaten_positions) + 
  tm_dots(id = "CRUISENO",
          col="red",
          popup.vars=c("Position_ID"="POSITION_ID","Camera"="CAMERA_NUMBER"))+
  tm_shape(Observations_positions) + 
  tm_dots(id = "CRUISENO",
          col="blue",
          popup.vars=c("Observation_ID"="OBSERVATION_ID","Specie"="ENGLISH_NAME"))+
  tm_layout(legend.bg.color = 'white',  #Label background
            legend.position = c(0.1,"bottom"),  #Label position
            legend.frame = TRUE) #Label frame
```

## Sightings

This map displays all **observations**, grouped by morphological/taxonomic category.
Each taxonomic group is represented by a distinct color:

Gulls in <span style="color: #565aa0;">light purple</span>; 
Skuas in <span style="color: #8ac926;">green</span>; 
Gannets and cormorants <span style="color: #ff924c;">orange</span>; 
Auks in <span style="color: #36949d;">grey blue</span>; 
Terns in <span style="color: #6a4c93;">purple</span>; 
Ducks and Shelducks in <span style="color: #ffca3a;">yellow</span>; 
Swans and Geese in <span style="color: #c5ca30;">green-yellow</span>; 
Divers in <span style="color: #ff595e;">red</span>; 
Grebes in <span style="color: #1982c4;">light blue</span>; 
Waders in <span style="color: #4267ac;">darkblue</span>; 
Other seabirds and other species in  <span style="color: #333533;">grey</span>; 
Marine mammals in  <span style="color: #a53860;">dark pink</span>;
Harbour porpoises in  <span style="color: #3c6e71;">dark green</span>, and also shown separated by adults and calves;
Other species in  <span style="color: #fb6f92;">pink</span>. 

```{r TaxGroup, include=FALSE, echo=FALSE, warnings=FALSE}
Euring_Tax<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)
Observations_animals<- Observations_sf %>% filter (ENGLISH_NAME != "0")
Observations_tax<-Observations_animals %>%
  left_join(Euring_Tax,by='ENGLISH_NAME')
Observations_tax<-Observations_tax %>%
  rename(Morphological_group=Artificial_tax_class)
```

```{r CheckGroups, include=FALSE, echo=FALSE}
Observations_tax %>%
  group_by(Morphological_group) %>%
  count(Morphological_group)
```

```{r LoadShapefiles, echo=FALSE, include=FALSE, eval=TRUE}
Areas<-st_transform(GermanNorthSea::Study_areas,4326)
Land<- st_transform(GermanNorthSea::German_land,4326)
SPA <- st_transform(GermanNorthSea::German_natura,4326)
SCA<- st_transform(GermanNorthSea::German_SCA,4326)
OWF<- st_transform(GermanNorthSea::OWF_EMODnet,4326)
```

```{r Base_map,echo=FALSE}
Base_map<- tm_shape(Areas)+  
  tm_polygons(col='#d62828', alpha=0.1,lty = "solid")+
  tm_shape(OWF)+  
  tm_polygons(col='#f77f00', alpha=0.1,lty = "dotted")+
  tm_shape(SPA)+  
  tm_polygons(col='#006d77', alpha=0.1,lty = "dashed")+
  tm_shape(SCA)+  
  tm_polygons(col='#006d77', alpha=0.1,lty = "dashed")
```


```{r AddGulls, echo=FALSE}
Add_gulls<-function(This_group=This_group){
  Gulls_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Gulls_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
        print(paste(This_group,"will be included in the map"))
        Base_map<-Base_map+
           tm_shape(Gulls_positions) + 
             tm_dots(id = "Morphological group",
                       col="#565aa0",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGulls, echo=FALSE, comment=NA}
Add_gulls(This_group='Gulls')
```

```{r AddSkuas, echo=FALSE}
Add_skuas<-function(This_group=This_group){
  Skuas_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Skuas_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
         print(paste(This_group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(Skuas_positions) + 
            tm_dots(id = "Morphological_group",
              col="#8ac926",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignSkuas, echo=FALSE, comment=NA}
Add_skuas(This_group="Skuas")
```

```{r AddGannets, echo=FALSE}
Add_gannets<-function(This_group=This_group){
  Gannets_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Gannets_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
          print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Gannets_positions) + 
             tm_dots(id = "Morphological group",
                       col="#ff924c",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGannets, echo=FALSE, comment=NA}
Add_gannets(This_group='Gannets_Cormorants')
```

```{r AddAuks, echo=FALSE}
Add_auks<-function(This_group=This_group){
  Auks_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Auks_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
         print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Auks_positions) + 
            tm_dots(id = "Morphological group",
              col="#36949d",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
    assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignAuks, echo=FALSE, comment=NA}
Add_auks(This_group="Auks")
```

```{r AddTerns, echo=FALSE}
Add_terns<-function(This_group=This_group){
  Terns_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Terns_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
          print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Terns_positions) + 
            tm_dots(id = "Morphological group",
                     col="#6a4c93",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignTerns, echo=FALSE, comment=NA}
Add_terns(This_group='Terns')
```

```{r AddDucks, echo=FALSE}
Add_ducks<-function(This_group=This_group){
  DucksShelducks_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(DucksShelducks_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
           print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(DucksShelducks_positions) + 
            tm_dots(id = "Morphological group",
                     col="#ffca3a",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignDucks,  echo=FALSE, comment=NA}
Add_ducks(This_group="Ducks_Shelducks")
```

```{r AddGeeseSwan,echo=FALSE}
Add_geese<-function(This_group=This_group){
 SwanGeese_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(SwanGeese_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
           print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(SwanGeese_positions) + 
            tm_dots(id = "Morphological group",
                     col="#c5ca30",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGesseSwan,  echo=FALSE, comment=NA}
Add_geese(This_group="Swan_Geese")
```

```{r AddDivers, echo=FALSE}
Add_divers<-function(This_group=This_group){
 Divers_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Divers_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
           print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Divers_positions) + 
            tm_dots(id = "Morphological group",
                     col="#ff595e",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignDivers, echo=FALSE, comment=NA}
Add_divers(This_group='Divers')
```

```{r AddGrebes, echo=FALSE}
Add_grebes<-function(This_group=This_group){
  Grebes_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Grebes_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
         print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Grebes_positions) + 
             tm_dots(id = "Morphological group",
                       col="#1982c4",
                       popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGrebes,  echo=FALSE, comment=NA}
Add_grebes(This_group='Grebes')
```

```{r AddWaders, echo=FALSE}
Add_waders<-function(This_group=This_group){
  Waders_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(Waders_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
          print(paste(This_group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Waders_positions) + 
             tm_dots(id = "Morphological group",
                       col="#4267ac",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignWaders, echo=FALSE, comment=NA}
Add_waders(This_group='Waders')
```

```{r AddSeabirds, echo=FALSE}
Add_seabirds<-function(This_group=This_group){
  OtherSeabirds_positions<-Observations_tax %>%
    filter(Observations_tax$Morphological_group==This_group)
    if(nrow(OtherSeabirds_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
         print(paste(This_group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(OtherSeabirds_positions) + 
            tm_dots(id = "Morphological group",
                     col="#333533",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
   assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssingSeabirds,  echo=FALSE, comment=NA}
Add_seabirds(This_group='Other_seabirds')
```

```{r AddMammals, echo=FALSE}
Add_mammals<-function(This_group=This_group){
 MarineMammals_positions<-Observations_tax %>%
   filter(Observations_tax$Morphological_group==This_group)%>%
   filter(OBSERVATION!=63510)
    if(nrow(MarineMammals_positions) == 0) {
        print(paste("No",This_group,"occurred in the survey"))
        } else {
          print(paste(This_group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(MarineMammals_positions) + 
            tm_dots(id = "Morphological group",
                     col="#a53860",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignMarineMammals,  echo=FALSE, comment=NA}
Add_mammals(This_group="Marine_mammals")
```

```{r AddHarbourPorpoise, echo=FALSE}
HarbourPorpoise_positions<-Observations_tax %>% filter(OBSERVATION==63510) 
if(nrow(HarbourPorpoise_positions) == 0) {
        print(paste("No Harbour porpoise occurred in the survey"))
        } else {
          print(paste("Harbour Porpoise will be included in the map"))
          Base_map<-Base_map+
           tm_shape(HarbourPorpoise_positions) + 
            tm_dots(id = "Morphological group",
                     col="#3c6e71",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
```
```{r AddHarbourPorpoiseAdults, echo=FALSE}
HarbourPorpoise_adults<-Observations_tax %>% filter(OBSERVATION==63510)%>%filter(AGE_CLASS=='A')
if(nrow(HarbourPorpoise_adults) == 0) {
        print(paste("No Harbour porpoise occurred in the survey"))
        } else {
          print(paste("Harbour Porpoise Adults will be included in the map"))
          Base_map<-Base_map+
           tm_shape(HarbourPorpoise_adults) + 
            tm_dots(id = "Morphological group",
                    shapes=16,
                     col='#c1121f',
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME","Age_class"="AGE_CLASS"))
  assign('Base_map',Base_map,envir=globalenv())}
```

```{r AddHarbourPorpoiseCalves, echo=FALSE}
HarbourPorpoise_calves<-Observations_tax %>% filter(OBSERVATION==63510)%>%filter(AGE_CLASS=='IM')
if(nrow(HarbourPorpoise_calves) == 0) {
        print(paste("No Harbour porpoise calves occurred in the survey"))
        } else {
          print(paste("Harbour Porpoise calves will be included in the map"))
          Base_map<-Base_map+
           tm_shape(HarbourPorpoise_calves) + 
            tm_dots(id = "Morphological group",
                    shapes=17,
                     col="#ffe100",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME","Age_class"="AGE_CLASS"))
  assign('Base_map',Base_map,envir=globalenv())}
```

```{r AddOthers, echo=FALSE}
NotIncluded <- subset(Observations_tax, is.na(Morphological_group))
Other_species <- subset(Observations_tax, Morphological_group == 'Other_species')
MissingSpecies_positions<-rbind(NotIncluded,Other_species)

if(nrow(MissingSpecies_positions) == 0) {
        print(paste("No other species occurred in the survey"))
        } else {
         print(paste("Other species will be included in the map"))
          Base_map<-Base_map+
           tm_shape(MissingSpecies_positions) + 
            tm_dots(id = "Morphological group",
                     col="#000814",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
```


You can interact with the map using the following controls:<br> 
Using `r fa("layer-group", fill = 'black')` to toogle **morphological** groups on and off.<br> 
Using `r fa("plus", fill = 'black')` to **zoom-in** and explore the points in more detail.<br>  
Using `r fa("minus", fill = 'black')` to **zoom-out** for a broader view.<br> 
Click on a point `r fa("mouse-pointer", fill = 'black')` to view the species information.<br> 

```{r Observations_map, echo=FALSE, warnings=FALSE, message=FALSE, comment=FALSE}
Base_map+
  tm_layout(legend.bg.color = 'white',
            legend.position = c(0.1,"bottom"), 
            legend.frame = TRUE) 
```



# End of document