---
title: "Separated Maps"
author: "Seabird Monitoring"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
  ThisDirectory: ThisDirectory
  ThisFile: ThisFile
  BasisDaten: BasisDaten
  Observations: Observations
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fontawesome)
```

# Intro

Using data from **`r params$ThisFile`** excel file.  
This document presents two maps:

- The first map shows the Survey Observations and base positions.

- The second map displays the sightings.

Please note that rendering may take some time due to the large number of points. Thank you for your patience.  ⏳

```{r Packages, echo=FALSE, warnings=FALSE}
library(sf)
library(tmap)
library(ggplot2)
library(tidyverse)
```

## Position accuracy

Basis position and Observations positions are plotted on the map.<br> 

Once the map has loaded, temporary **unselect** the layer BP (Basis Points).<br>  
Then, zoom into your area of interest using the blue dots as a reference.<br> 
After zooming, re-enable the BP layer.<br> 
This saves rendering time.<br> 

Points shown in  <span style="color: #ff595e;">red</span> represent data from **Basis**, based on their longitude and latitude.<br>
Points shown in <span style="color: #1982c4;"> blue</span>represent data from **Observations**, based on their longitude and latitude. <br> 

You can interact with the map using the following controls:<br> 
Using `r fa("plus", fill = 'black')` **zoom-in** to examine points in detail.<br> 
Using `r fa("minus", fill = 'black')` **zoom-out** for a broader view.<br>  
Using `r fa("layer-group", fill = 'black')` toogle **layers** on and off.<br>  
Hover over a blue dot with the cursor `r fa("mouse-pointer", fill = 'black')` When the icon changes to `r fa("hand-point-up", fill = 'black')`, click it to view the position ID and species information.<br> 


```{r Parameters, include=FALSE, echo=FALSE, eval=TRUE}
Maps_BasisDaten<-params$BasisDaten
Maps_Observations<-params$Observations
```

```{r Manual, echo=FALSE, eval=FALSE}
Maps_BasisDaten<-BasisDaten
Maps_Observations<-Observations
```

```{r BasisLayer, echo=FALSE}
BasisDaten_df<-Maps_BasisDaten
BasisDaten_df$lat<-as.numeric(BasisDaten_df$LAT_PIC_CENTER)
BasisDaten_df$lon<-as.numeric(BasisDaten_df$LON_PIC_CENTER)
BasisDaten_df <- BasisDaten_df[!is.na(BasisDaten_df$lat) & !is.na(BasisDaten_df$lon), ] 
BasisDaten_sf <- st_as_sf(BasisDaten_df, coords = c("lon", "lat"),crs = 4326, agr = "constant")
```

```{r ObservationsLayer, echo=FALSE}
Observations_df<-Maps_Observations
Observations_df$lat<-as.numeric(Observations_df$LAT_OBJECT)
Observations_df$lon<-as.numeric(Observations_df$LON_OBJECT)
Observations_df <- Observations_df[!is.na(Observations_df$lat) & !is.na(Observations_df$lon), ] 
Observations_sf <- st_as_sf(Observations_df, coords = c("lon", "lat"),crs = 4326, agr = "constant")
```

```{r DisplayedInformation, echo=FALSE, eval=FALSE}
BasisDaten_positions<-BasisDaten_sf[,c("POSITION_ID","CAMERA_NUMBER")]
Observations_positions<-Observations_sf[,c("OBSERVATION_ID","ENGLISH_NAME")]
```

```{r View, echo=FALSE, include=FALSE, eval=TRUE}
tmap_mode("view") #interactive tmap_mode("view")
```

```{r BasisMap, echo=FALSE, include=TRUE, warning=FALSE, message=FALSE, eval=TRUE}
tm_shape(BasisDaten_positions) + 
  tm_dots(id = "CRUISENO",
          col="red",
          popup.vars=c("Position_ID"="POSITION_ID","Camera"="CAMERA_NUMBER"))+
  tm_shape(Observations_positions) + 
  tm_dots(id = "CRUISENO",
          col="blue",
          popup.vars=c("Observation_ID"="OBSERVATION_ID","Specie"="ENGLISH_NAME"))+
  tm_layout(legend.bg.color = 'white',  #Label background
            legend.position = c(0.1,"bottom"),  #Label position
            legend.frame = TRUE) #Label frame
```

## Sightings

This map displays all **observations**, grouped by morphological/taxonomic category.
Each taxonomic group is represented by a distinct color:

Ducks and Shelducks in <span style="color: #ffca3a;">yellow</span>; 
Swans and Geese in <span style="color: #c5ca30;">green-yellow</span>; 
Divers in <span style="color: #ff595e;">red</span>; 
Grebes in <span style="color: #1982c4;">light blue</span>; 
Gannets and cormorants <span style="color: #ff924c;">orange</span>; 
Auks in <span style="color: #36949d;">grey blue</span>; 
Gulls in <span style="color: #565aa0;">light purple</span>; 
Skuas in <span style="color: #8ac926;">green</span>; 
Terns in <span style="color: #6a4c93;">purple</span>; 
Waders in <span style="color: #4267ac;">darkblue</span>; 
Other seabirds and other species in  <span style="color: #333533;">grey</span>; 
Marine mammals in  <span style="color: #202020;">black</span>.


```{r TaxGroup, include=FALSE, echo=FALSE, warnings=FALSE}
Euring_Tax<-seamonas::Code_Euring %>%
  rename(ENGLISH_NAME=English_name)
Observations_animals<- Observations_sf %>% filter (ENGLISH_NAME != "0")
Observations_tax<-Observations_animals %>%
  left_join(Euring_Tax,by='ENGLISH_NAME')
Observations_tax<-Observations_tax %>%
  rename(Groups=Artificial_tax_class)
```

```{r CheckGroups, include=FALSE, echo=FALSE}
Observations_tax %>%
  group_by(Groups) %>%
  count(Groups)
```

```{r LoadShapefiles, echo=FALSE, include=FALSE, eval=TRUE}
Areas<-st_transform(GermanNorthSea::Study_areas,4326)
Land<- st_transform(GermanNorthSea::German_land,4326)
SPA <- st_transform(GermanNorthSea::German_natura,4326)
SCA<- st_transform(GermanNorthSea::German_SCA,4326)
OWF<- st_transform(GermanNorthSea::OWF_EMODnet,4326)
```

```{r Base_map,echo=FALSE}
Base_map<- tm_shape(Areas)+  
  tm_polygons(col='#d62828', alpha=0.1,lty = "solid")+
  tm_shape(OWF)+  
  tm_polygons(col='#f77f00', alpha=0.1,lty = "dotted")+
  tm_shape(SPA)+  
  tm_polygons(col='#006d77', alpha=0.1,lty = "dashed")+
  tm_shape(SCA)+  
  tm_polygons(col='#006d77', alpha=0.1,lty = "dashed")
```


```{r AddGulls, echo=FALSE}
Add_gulls<-function(Group=Group){
  Gulls_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Gulls_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         print(paste(Group,"will be included in the map"))
        Base_map<-Base_map+
           tm_shape(Gulls_positions) + 
             tm_dots(id = "TaxGroups",
                       col="#565aa0",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGulls, echo=FALSE, comment=NA}
Add_gulls(Group='Gulls')
```

```{r AddSkuas, echo=FALSE}
Add_skuas<-function(Group=Group){
  Skuas_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Skuas_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         print(paste(Group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(Skuas_positions) + 
            tm_dots(id = "TaxGroups",
              col="#8ac926",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('BasMap',Base_map,envir=globalenv())}
  }
```

```{r AssignSkuas, echo=FALSE, comment=NA}
Add_skuas(Group="Skuas")
```

```{r AddGannets, echo=FALSE}
Add_gannets<-function(Group=Group){
  Gannets_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Gannets_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
          print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Gannets_positions) + 
             tm_dots(id = "TaxGroups",
                       col="#ff924c",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGannets, echo=FALSE, comment=NA}
Add_gannets(Group='Gannets_Cormorants')
```

```{r AddAuks, echo=FALSE}
Add_auks<-function(Group=Group){
  Auks_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Auks_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Auks_positions) + 
            tm_dots(id = "TaxGroups",
              col="#36949d",
                popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
    assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignAuks, echo=FALSE, comment=NA}
Add_auks(Group="Auks")
```

```{r AddTerns, echo=FALSE}
Add_terns<-function(Group=Group){
  Terns_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Terns_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
          print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Terns_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#6a4c93",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignTerns, echo=FALSE, comment=NA}
Add_terns(Group='Terns')
```

```{r AddDucks, echo=FALSE}
Add_ducks<-function(Group=Group){
  DucksShelducks_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(DucksShelducks_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
           print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(DucksShelducks_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#ffca3a",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
         #_positionsstitutes base map adding the layer
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignDucks,  echo=FALSE, comment=NA}
Add_ducks(Group="Ducks_Shelducks")
```

```{r AddGeeseSwan,echo=FALSE}
Add_geese<-function(Group=Group){
 SwanGeese_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(SwanGeese_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
           print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(SwanGeese_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#c5ca30",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGesseSwan,  echo=FALSE, comment=NA}
Add_geese(Group="Swan_Geese")
```

```{r AddDivers, echo=FALSE}
Add_divers<-function(Group=Group){
 Divers_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Divers_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
           print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Divers_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#ff595e",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignDivers, echo=FALSE, comment=NA}
Add_divers(Group='Divers')
```

```{r AddGrebes, echo=FALSE}
Add_grebes<-function(Group=Group){
  Grebes_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Grebes_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
          print(paste(Group,"will be included in the map"))
         Base_map<-Base_map+
           tm_shape(Grebes_positions) + 
             tm_dots(id = "TaxGroups",
                       col="#1982c4",
                       popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignGrebes,  echo=FALSE, comment=NA}
Add_grebes(Group='Grebes')
```

```{r AddWaders, echo=FALSE}
Add_waders<-function(Group=Group){
  Waders_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(Waders_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         Base_map<-Base_map+
           tm_shape(Waders_positions) + 
             tm_dots(id = "TaxGroups",
                       col="#4267ac",
                        popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignWaders, echo=FALSE, comment=NA}
Add_waders(Group='Waders')
```

```{r AddSeabirds, echo=FALSE}
Add_seabirds<-function(Group=Group){
  OtherSeabirds_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(OtherSeabirds_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         print(paste(Group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(OtherSeabirds_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#333533",
                      popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
   assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssingSeabirds,  echo=FALSE, comment=NA}
Add_seabirds(Group='Other_seabirds')
```

```{r AddOthers, echo=FALSE}
Add_others<-function(Group=Group){
  OtherBirds_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(OtherBirds_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
         print(paste(Group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(OtherBirds_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#333533",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignOthers,  echo=FALSE, comment=NA}
Add_others(Group='Other_species')
```

```{r AddMammals, echo=FALSE}
Add_mammals<-function(Group=Group){
 MarineMammals_positions<-Observations_tax %>%
    filter(Observations_tax$Groups==Group)
    if(nrow(MarineMammals_positions) == 0) {
        print(paste("No",Group,"occurred in the survey"))
        } else {
          print(paste(Group,"will be included in the map"))
          Base_map<-Base_map+
           tm_shape(MarineMammals_positions) + 
            tm_dots(id = "TaxGroups",
                     col="#202020",
                     popup.vars=c("Position_ID"="POSITION_ID","Specie"="ENGLISH_NAME"))
  assign('Base_map',Base_map,envir=globalenv())}
  }
```

```{r AssignMarineMammals,  echo=FALSE, comment=NA}
Add_mammals(Group="Marine_mammals")
```

You can interact with the map using the following controls:<br> 
Using `r fa("layer-group", fill = 'black')` to toogle **morphological** groups on and off.<br> 
Using `r fa("plus", fill = 'black')` to **zoom-in** and explore the points in more detail.<br>  
Using `r fa("minus", fill = 'black')` to **zoom-out** for a broader view.<br> 
Click on a point `r fa("mouse-pointer", fill = 'black')` to view the species information.<br> 

```{r Observations_map, echo=FALSE, warnings=FALSE, message=FALSE, comment=FALSE}
Base_map+
  tm_layout(legend.bg.color = 'white',
            legend.position = c(0.1,"bottom"), 
            legend.frame = TRUE) 
```



# End of document