---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Quality Checks

This repository includes the parametrized script to run Quality Checks in R.

To use:

1. Open the **project** QualityCheck

2. Open the Rmd 00QualityCheck

Before running the script the following packages are required

To install

```{r, eval=FALSE}
#For reading data
install.packages("here") #for assigning directory in a project
install.packages("readxl") #for reading excelsheet
install.packages("tidyverse") #for data wrangling
install.packages("beepr") #for making a noise when ready

#For report
install.packages("knitr") #for exporting tables in word
install.packages("kableExtra") #for arranging tables in word
install.packages("ggplot2") #for making plots
install.packages("sp") #for reading shapefiles
install.packages("sf") #for plotting shapefiles

install.packages("devtools")
devtools::install_github("MiriamLL/GermanNorthSea") #for loading shapefiles
devtools::install_github("MiriamLL/seamonas") #for accessing Euring information

#For Dinamic maps 
install.packages("tmap") #for creating maps with layers
install.packages("fontawesome") #for adding icons
```

## 00QualityCheck

### Reading the files

The script is about reading your data.
It is parametrized that the data should be in the folder 00Data, either copy your file to this folder, o give the direction.

The sheets in the excelfile should be organized as:
1. Tripdaten
2. Basisdaten
3. Observations
Please provide this order and this names for the sheets.

### Running the formal check validation

Basically, as it is an Rmd you would just need to run the script or click on the green play (triangle) symbol to run.

#### 01FormalCheckandDataValidation
Checks that the column names are completely filled and that they fit their expected names.  
It also checks that mandatory columns are fully filled, and for the non-mandatory calculates how many where filled.  
Moreover, it checks which values were used in each column, and compares with the expected values.  

##### Trip Daten

Reproduce test data

```{r}
library(tidyverse)
```

```{r}
TripDaten_test<-data.frame(TRIP=NA,
                       TRIP_ID='1',
                       Dataset_ID='1',
                       CRUISENO='AreaA_Summer_2025',
                       OWPAS='ClientName',
                       PROJECT='ProjectName',
                       CLUSTER='A',
                       LAB='CompanyName',
                       SCIENTIST='ResponsibleName',
                       DATATYPE='SeabirdMonitoring',
                       TECHNIQUE='Video',
                       OBSERVER='FlyingCompany',
                       PLANE='TypeOfPlane',
                       NUMBER_OF_PLANES=1,
                       DOUBLE_PLATFORM='No',
                       DATE='20250616',
                       STARTTIME='09:00:00',
                       ENDTIME='11:00:00',
                       CAMERA_SYSTEM='CameraSystemSpecifications',
                       RESOLUTION=2,
                       PLANE_FLIGHT_HEIGHT_PLANNED=540,
                       STRIP_WIDTH=400,
                       PLANE_SPEED=100,
                       POSITION_ACCURACY=50,
                       METHOD_ID=1,
                       AREA_OBSERVED=100,
                       AREA_ANALYSED=80,
                       AREA_CONTROLLED=25,
                       ID_CONTROLLED=300,
                       SCREENING_CONTROL_DIFFERENCE=15,
                       ID_CONTROL_DIFFERENCE=20,
                       QUALITY_IMPROVEMENT='Reassessment of species identification when observer had biases in auks',
                       POSITIONSYSTEM='GPS',
                       POSIT_PRECISION_CODE=1,
                       REFSYSTEM='WGS84',
                       NOTES=NA
                       )
```

#### Basis Daten

Reproduce test data

Transect lat and long

```{r}
LAT_PIC_CENTER<-c(54.16421,54.16470,54.16515,54.16567,54.16403,54.16455,54.16500,54.16549,54.16358,54.16411,
                  54.16460,54.16516,54.16339,54.16395,54.16444,54.16497,54.16298,54.16353,54.16405,54.16465,
                  54.16277,54.16336,54.16389,54.16444,54.16238,54.16297,54.16351,54.16413,54.16217,54.16279,
                  54.16334,54.16392,54.16181,54.16241,54.16297,54.16362,54.16159,54.16223,54.16279,54.16339,
                  54.16126,54.16187,54.16244,54.16309,54.16103,54.16168,54.16225,54.16286,54.16072,54.16133,
                  54.16190,54.16256,54.16049,54.16115,54.16172,54.16233,54.16020,54.16080,54.16137,54.16202,
                  54.15997,54.16062,54.16119,54.16180,54.15969,54.16028,54.16084,54.16148,54.15947,54.16010,
                  54.16066,54.16126,54.15919,54.15977,54.16031,54.16092,54.15898,54.15959,54.16013,54.16071,
                  54.15870,54.15925,54.15977,54.16035,54.15850,54.15909,54.15960,54.16015,54.15821,54.15873,
                  54.15922,54.15978,54.15802,54.15858,54.15907,54.15959,54.15771,54.15821,54.15868,54.15921,
                  54.15752,54.15806,54.15853,54.15903,54.15720,54.15768,54.15813,54.15864,54.15702,54.15753,
                  54.15798,54.15846,54.15668,54.15714,54.15758,54.15807,54.15650,54.15700,54.15743,54.15790,
                  54.15615,54.15660,54.15702,54.15750,54.15598,54.15646,54.15689,54.15734,54.15561,54.15606,
                  54.15647,54.15694,54.15545,54.15592,54.15633,54.15677,54.15507,54.15550,54.15591,54.15637,
                  54.15491,54.15537,54.15578,54.15621,54.15452,54.15495,54.15535,54.15581,54.15437,54.15482,
                  54.15522,54.15565,54.15397,54.15440,54.15479,54.15525,54.15381,54.15427,54.15467,54.15509,
                  54.15341,54.15384,54.15423,54.15469,54.15325,54.15371,54.15411,54.15453,54.15285,54.15328,
                  54.15368,54.15414,54.15269,54.15315,54.15355,54.15398,54.15229,54.15272,54.15312,54.15358,
                  54.15213,54.15259,54.15299,54.15342,54.15172,54.15216,54.15256,54.15302,54.15156,54.15203,
                  54.15243,54.15286,54.15116,54.15160,54.15200,54.15247,54.15100,54.15147,54.15187,54.15231,
                  54.15060,54.15104,54.15144,54.15191,54.15044,54.15090,54.15131,54.15175,54.15004,54.15048,
                  54.15089,54.15136,54.14987,54.15034,54.15075,54.15120,54.14947,54.14992,54.15033,54.15080,
                  54.14931,54.14978,54.15020,54.15064,54.14891,54.14936,54.14977,54.15025,54.14875,54.14923,
                  54.14964,54.15009,54.14835,54.14880,54.14922,54.14970,54.14819,54.14867,54.14908,54.14953,
                  54.14779,54.14824,54.14867,54.14915,54.14763,54.14811,54.14853,54.14898,54.14724,54.14769,
                  54.14811,54.14860,54.14707,54.14755,54.14798,54.14843,54.14668,54.14714,54.14756,54.14805,
                  54.14651,54.14700,54.14742,54.14788,54.14613,54.14658,54.14701,54.14750,54.14596,54.14645,
                  54.14687,54.14733,54.14558,54.14603,54.14646,54.14694,54.14541,54.14590,54.14632,54.14678,
                  54.14504,54.14549,54.14591,54.14639,54.14487,54.14535,54.14577,54.14623,54.14449,54.14494,
                  54.14536,54.14584,54.14433,54.14481,54.14522,54.14567,54.14395,54.14440,54.14481,54.14528,
                  54.14379,54.14426,54.14468,54.14512,54.14341,54.14385,54.14426,54.14473,54.14325,54.14372,
                  54.14413,54.14456,54.14288,54.14331,54.14371,54.14417,54.14272,54.14318,54.14358,54.14401,
                  54.14235,54.14277,54.14316,54.14360,54.14219,54.14264,54.14303,54.14345,54.14182,54.14222,
                  54.14260,54.14304,54.14167,54.14210,54.14248,54.14289,54.14128,54.14168,54.14205,54.14247,
                  54.14114,54.14156,54.14193,54.14233,54.14075,54.14113,54.14150,54.14191,54.14060,54.14102,
                  54.14138,54.14177,54.14021,54.14059,54.14094,54.14135,54.14006,54.14047,54.14083,54.14121,
                  54.13966,54.14004,54.14039,54.14079,54.13952,54.13992,54.14028,54.14065,54.13911,54.13949,
                  54.13984,54.14023,54.13898,54.13938,54.13972,54.14010,54.13856,54.13893,54.13928,54.13968,
                  54.13843,54.13882,54.13917,54.13954,54.13801,54.13838,54.13873,54.13913,54.13787,54.13827,
                  54.13862,54.13899,54.13745,54.13783,54.13818,54.13858,54.13731,54.13771,54.13806,54.13844,
                  54.13689,54.13727,54.13762,54.13803,54.13675,54.13716,54.13751,54.13789,54.13633,54.13671,
                  54.13707,54.13748,54.13618,54.13660,54.13696,54.13734,54.13576,54.13615,54.13652,54.13694,
                  54.13562,54.13604,54.13640,54.13679,54.13520,54.13560,54.13597,54.13640,54.13505,54.13548,
                  54.13585,54.13625,54.13464,54.13504,54.13542,54.13585,54.13448,54.13492,54.13530,54.13570,
                  54.13407,54.13448,54.13486,54.13530,54.13392,54.13436,54.13474,54.13515,54.13351,54.13393,
                  54.13431,54.13475,54.13336,54.13380,54.13419,54.13460,54.13296,54.13337,54.13376,54.13420,
                  54.13280,54.13325,54.13363,54.13405,54.13240,54.13282,54.13320,54.13365,54.13224,54.13269,
                  54.13308,54.13350,54.13184,54.13226,54.13265,54.13310,54.13169,54.13213,54.13252,54.13294,
                  54.13128,54.13170,54.13209,54.13254,54.13113,54.13158,54.13197,54.13239,54.13073,54.13115,
                  54.13153,54.13198,54.13057,54.13102,54.13141,54.13183,54.13017,54.13059,54.13097,54.13142,
                  54.13002,54.13046,54.13085,54.13126,54.12962,54.13003,54.13041,54.13085,54.12946,54.12990,
                  54.13029,54.13070,54.12906,54.12947,54.12985,54.13029,54.12890,54.12934,54.12973,54.13014,
                  54.12849,54.12890,54.12929,54.12973,54.12834,54.12878,54.12916,54.12958,54.12793,54.12834,
                  54.12872,54.12916,54.12778,54.12822,54.12860,54.12901,54.12736,54.12777,54.12816,54.12860,
                  54.12721,54.12765,54.12803,54.12845,54.12680,54.12721,54.12759,54.12803,54.12664,54.12709,
                  54.12747,54.12788,54.12623,54.12664,54.12703,54.12747,54.12608,54.12652,54.12691,54.12732,
                  54.12566,54.12608,54.12647,54.12691,54.12550,54.12595,54.12634,54.12676,54.12509,54.12551,
                  54.12590,54.12635,54.12493,54.12538,54.12578,54.12620,54.12452,54.12494,54.12534,54.12579,
                  54.12436,54.12482,54.12521,54.12564,54.12395,54.12438,54.12478,54.12524,54.12379,54.12425,
                  54.12465,54.12508,54.12339,54.12382,54.12422,54.12468,54.12323,54.12369,54.12409,54.12452,
                  54.12282,54.12326,54.12366,54.12413,54.12266,54.12313,54.12353,54.12397,54.12226,54.12270,
                  54.12311,54.12357,54.12210,54.12257,54.12297,54.12341,54.12171,54.12214,54.12255,54.12301,
                  54.12155,54.12201,54.12242,54.12285,54.12116,54.12159,54.12199,54.12245,54.12100,54.12146,
                  54.12186,54.12229,54.12061,54.12104,54.12144,54.12189,54.12045,54.12091,54.12131,54.12174,
                  54.12006,54.12049,54.12088,54.12133,54.11991,54.12036,54.12076,54.12118,54.11952,54.11994,
                  54.12033,54.12077,54.11937,54.11981,54.12020,54.12062,54.11898,54.11939,54.11977,54.12021,
                  54.11883,54.11927,54.11965,54.12006,54.11845,54.11885,54.11922,54.11964,54.11830,54.11873,
                  54.11910,54.11950,54.11791,54.11830,54.11866,54.11908,54.11776,54.11818,54.11855,54.11894,
                  54.11737,54.11775,54.11811,54.11852,54.11723,54.11764,54.11800,54.11838,54.11683,54.11721,
                  54.11756,54.11796,54.11669,54.11709,54.11744,54.11782,54.11628,54.11666,54.11701,54.11741,
                  54.11615,54.11655,54.11689,54.11727,54.11574,54.11611,54.11646,54.11685,54.11560,54.11600,
                  54.11634,54.11672,54.11519,54.11556,54.11590,54.11630,54.11505,54.11545,54.11579,54.11617,
                  54.11464,54.11501,54.11536,54.11575,54.11450,54.11490,54.11524,54.11562,54.11408,54.11446,
                  54.11481,54.11521,54.11394,54.11435,54.11469,54.11507,54.11353,54.11391,54.11426,54.11467,
                  54.11339,54.11379,54.11415,54.11453,54.11297,54.11335,54.11371,54.11412,54.11283,54.11324,
                  54.11360,54.11398,54.11241,54.11280,54.11317,54.11359,54.11226,54.11268,54.11305,54.11344,
                  54.11185,54.11225,54.11262,54.11305,54.11170,54.11213,54.11250,54.11290,54.11129,54.11170,
                  54.11208,54.11251,54.11114,54.11158,54.11196,54.11236,54.11074,54.11115,54.11153,54.11197,
                  54.11058,54.11102,54.11141,54.11182,54.11018,54.11060,54.11099,54.11144,54.11003,54.11047,
                  54.11086,54.11128,54.10963,54.11005,54.11045,54.11090,54.10947,54.10992,54.11032,54.11074,
                  54.10907,54.10950,54.10990,54.11036,54.10892,54.10938,54.10977,54.11020,54.10853,54.10896,
                  54.10936,54.10983,54.10836,54.10883,54.10923,54.10967,54.10798,54.10841,54.10882,54.10929,
                  54.10781,54.10828,54.10869,54.10913,54.10743,54.10787,54.10828,54.10876,54.10726,54.10774,
                  54.10815,54.10859,54.10688,54.10733,54.10775,54.10822,54.10672,54.10719,54.10761,54.10806,
                  54.10634,54.10679,54.10721,54.10769,54.10617,54.10665,54.10707,54.10752,54.10580,54.10625,
                  54.10667,54.10716,54.10563,54.10611,54.10654,54.10699,54.10525,54.10571,54.10614,54.10662,
                  54.10509,54.10557,54.10600,54.10646,54.10472,54.10518,54.10560,54.10609,54.10455,54.10504,
                  54.10547,54.10592,54.10418,54.10464,54.10507,54.10556,54.10401,54.10450,54.10493,54.10539,
                  54.10365,54.10411,54.10453,54.10502,54.10348,54.10397,54.10440,54.10486,54.10312,54.10357,
                  54.10400,54.10449,54.10295,54.10344,54.10386,54.10432,54.10259,54.10304,54.10347,54.10396,
                  54.10242,54.10291,54.10333,54.10379,54.10206,54.10251,54.10294,54.10342,54.10189,54.10238,
                  54.10280,54.10325,54.10153,54.10198,54.10240,54.10289,54.10136,54.10185,54.10227,54.10272,
                  54.10101,54.10145,54.10187,54.10235,54.10084,54.10132,54.10174,54.10218,54.10048,54.10092,
                  54.10134,54.10182,54.10031,54.10079,54.10121,54.10165,54.09995,54.10039,54.10081,54.10128,
                  54.09978,54.10026,54.10067,54.10112,54.09942,54.09986,54.10027,54.10075,54.09925,54.09973,
                  54.10014,54.10058,54.09889,54.09933,54.09974,54.10022,54.09872,54.09920,54.09961,54.10005,
                  54.09835,54.09880,54.09921,54.09969,54.09819,54.09866,54.09908,54.09952,54.09782,54.09826,
                  54.09868,54.09916,54.09766,54.09813,54.09855,54.09899,54.09728,54.09773,54.09815,54.09863,
                  54.09712,54.09760,54.09801,54.09846,54.09675,54.09720,54.09762,54.09810,54.09658,54.09706,
                  54.09748,54.09793,54.09621,54.09666,54.09709,54.09757,54.09604,54.09653,54.09695,54.09740)
```

```{r}
LON_PIC_CENTER<-c(8.622593,8.619760,8.617118,8.614090,8.623639,8.620611,8.617969,8.615135,8.622392,8.619583,
                  8.616963,8.613961,8.623428,8.620426,8.617807,8.614998,8.622153,8.619364,8.616764,8.613783,
                  8.623182,8.620201,8.617601,8.614812,8.621883,8.619109,8.616523,8.613559,8.622906,8.619942,
                  8.617356,8.614582,8.621586,8.618823,8.616246,8.613293,8.622605,8.619652,8.617076,8.614313,
                  8.621267,8.618509,8.615937,8.612989,8.622285,8.619336,8.616765,8.614007,8.620930,8.618171,
                  8.615599,8.612651,8.621948,8.618999,8.616427,8.613669,8.620579,8.617815,8.615238,8.612283,
                  8.621599,8.618645,8.616067,8.613303,8.620218,8.617443,8.614856,8.611890,8.621242,8.618276,
                  8.615689,8.612914,8.619850,8.617060,8.614459,8.611476,8.620880,8.617898,8.615296,8.612506,
                  8.619481,8.616673,8.614055,8.611053,8.620517,8.617516,8.614898,8.612090,8.619128,8.616304,
                  8.613671,8.610652,8.620171,8.617152,8.614519,8.611695,8.618794,8.615956,8.613311,8.610277,
                  8.619841,8.616808,8.614162,8.611325,8.618476,8.615628,8.612972,8.609927,8.619528,8.616483,
                  8.613827,8.610978,8.618174,8.615317,8.612652,8.609598,8.619229,8.616175,8.613510,8.610653,
                  8.617887,8.615022,8.612351,8.609289,8.618944,8.615882,8.613211,8.610347,8.617612,8.614742,
                  8.612067,8.608999,8.618671,8.615604,8.612928,8.610059,8.617348,8.614475,8.611797,8.608726,
                  8.618408,8.615338,8.612659,8.609787,8.617094,8.614220,8.611540,8.608468,8.618155,8.615083,
                  8.612403,8.609529,8.616848,8.613974,8.611295,8.608223,8.617909,8.614837,8.612157,8.609284,
                  8.616609,8.613737,8.611059,8.607989,8.617668,8.614599,8.611921,8.609049,8.616370,8.613501,
                  8.610826,8.607760,8.617429,8.614363,8.611688,8.608819,8.616131,8.613265,8.610593,8.607529,
                  8.617188,8.614125,8.611453,8.608587,8.615889,8.613026,8.610357,8.607298,8.616945,8.613886,
                  8.611217,8.608354,8.615646,8.612787,8.610121,8.607065,8.616701,8.613645,8.610979,8.608120,
                  8.615401,8.612546,8.609883,8.606831,8.616455,8.613403,8.610740,8.607885,8.615155,8.612303,
                  8.609644,8.606595,8.616208,8.613159,8.610500,8.607648,8.614908,8.612060,8.609404,8.606358,
                  8.615960,8.612915,8.610259,8.607410,8.614660,8.611815,8.609162,8.606120,8.615711,8.612669,
                  8.610016,8.607170,8.614412,8.611569,8.608918,8.605879,8.615461,8.612422,8.609772,8.606929,
                  8.614163,8.611322,8.608674,8.605637,8.615211,8.612175,8.609526,8.606686,8.613913,8.611074,
                  8.608427,8.605392,8.614960,8.611926,8.609279,8.606440,8.613659,8.610821,8.608175,8.605141,
                  8.614707,8.611673,8.609027,8.606189,8.613404,8.610565,8.607919,8.604884,8.614451,8.611417,
                  8.608771,8.605932,8.613146,8.610306,8.607658,8.604622,8.614194,8.611159,8.608511,8.605671,
                  8.612887,8.610045,8.607395,8.604356,8.613936,8.610898,8.608248,8.605406,8.612627,8.609782,
                  8.607129,8.604087,8.613678,8.610636,8.607983,8.605138,8.612368,8.609518,8.606861,8.603816,
                  8.613419,8.610374,8.607717,8.604867,8.612108,8.609254,8.606593,8.603543,8.613162,8.610111,
                  8.607450,8.604596,8.611850,8.608991,8.606325,8.603269,8.612905,8.609849,8.607183,8.604324,
                  8.611593,8.608728,8.606058,8.602996,8.612650,8.609588,8.606918,8.604053,8.611338,8.608468,
                  8.605792,8.602724,8.612398,8.609330,8.606653,8.603783,8.611090,8.608215,8.605534,8.602460,
                  8.612152,8.609078,8.606397,8.603522,8.610852,8.607972,8.605288,8.602210,8.611915,8.608837,
                  8.606152,8.603273,8.610622,8.607739,8.605052,8.601971,8.611686,8.608605,8.605917,8.603035,
                  8.610399,8.607515,8.604826,8.601743,8.611463,8.608381,8.605691,8.602807,8.610182,8.607298,
                  8.604608,8.601524,8.611247,8.608164,8.605474,8.602589,8.609971,8.607087,8.604397,8.601314,
                  8.611036,8.607953,8.605263,8.602378,8.609765,8.606881,8.604193,8.601111,8.610829,8.607747,
                  8.605058,8.602175,8.609561,8.606680,8.603994,8.600914,8.610624,8.607545,8.604858,8.601977,
                  8.609359,8.606482,8.603798,8.600723,8.610421,8.607345,8.604662,8.601785,8.609158,8.606285,
                  8.603607,8.600535,8.610219,8.607148,8.604469,8.601596,8.608956,8.606089,8.603415,8.600350,
                  8.610015,8.606950,8.604276,8.601408,8.608748,8.605886,8.603217,8.600158,8.609804,8.606745,
                  8.604076,8.601214,8.608532,8.605676,8.603013,8.599960,8.609587,8.606534,8.603870,8.601014,
                  8.608311,8.605460,8.602802,8.599755,8.609363,8.606316,8.603658,8.600807,8.608084,8.605239,
                  8.602586,8.599545,8.609134,8.606093,8.603441,8.600595,8.607852,8.605013,8.602365,8.599330,
                  8.608900,8.605865,8.603218,8.600378,8.607616,8.604782,8.602139,8.599110,8.608662,8.605632,
                  8.602990,8.600156,8.607375,8.604546,8.601909,8.598885,8.608419,8.605396,8.602758,8.599930,
                  8.607131,8.604307,8.601675,8.598657,8.608173,8.605155,8.602523,8.599699,8.606883,8.604065,
                  8.601438,8.598426,8.607923,8.604911,8.602284,8.599466,8.606633,8.603820,8.601198,8.598191,
                  8.607671,8.604665,8.602042,8.599230,8.606383,8.603576,8.600958,8.597958,8.607419,8.604418,
                  8.601801,8.598994,8.606134,8.603333,8.600721,8.597727,8.607168,8.604174,8.601562,8.598761,
                  8.605886,8.603091,8.600485,8.597498,8.606917,8.603930,8.601324,8.598530,8.605639,8.602851,
                  8.600251,8.597271,8.606668,8.603688,8.601088,8.598300,8.605392,8.602611,8.600018,8.597045,
                  8.606419,8.603446,8.600853,8.598072,8.605147,8.602372,8.599786,8.596820,8.606170,8.603205,
                  8.600618,8.597844,8.604901,8.602134,8.599553,8.596595,8.605923,8.602965,8.600384,8.597617,
                  8.604656,8.601895,8.599321,8.596370,8.605675,8.602724,8.600150,8.597389,8.604411,8.601657,
                  8.599089,8.596145,8.605428,8.602484,8.599915,8.597161,8.604166,8.601418,8.598855,8.595918,
                  8.605180,8.602243,8.599680,8.596932,8.603920,8.601177,8.598620,8.595688,8.604932,8.602000,
                  8.599443,8.596701,8.603669,8.600931,8.598378,8.595451,8.604680,8.601753,8.599200,8.596462,
                  8.603415,8.600680,8.598130,8.595206,8.604425,8.601501,8.598951,8.596216,8.603159,8.600425,
                  8.597876,8.594955,8.604167,8.601246,8.598697,8.595964,8.602900,8.600167,8.597619,8.594698,
                  8.603908,8.600987,8.598439,8.595706,8.602639,8.599906,8.597358,8.594436,8.603648,8.600727,
                  8.598178,8.595445,8.602378,8.599644,8.597094,8.594172,8.603387,8.600465,8.597915,8.595181,
                  8.602117,8.599381,8.596829,8.593904,8.603127,8.600202,8.597651,8.594914,8.601856,8.599117,
                  8.596563,8.593635,8.602868,8.599940,8.597385,8.594646,8.601597,8.598855,8.596297,8.593365,
                  8.602610,8.599678,8.597120,8.594378,8.601340,8.598593,8.596032,8.593096,8.602354,8.599418,
                  8.596857,8.594110,8.601090,8.598339,8.595775,8.592835,8.602105,8.599165,8.596600,8.593850,
                  8.600848,8.598095,8.595527,8.592584,8.601864,8.598921,8.596354,8.593601,8.600614,8.597858,
                  8.595289,8.592344,8.601631,8.598686,8.596116,8.593361,8.600387,8.597630,8.595059,8.592113,
                  8.601404,8.598457,8.595887,8.593130,8.600165,8.597408,8.594837,8.591889,8.601183,8.598235,
                  8.595664,8.592907,8.599948,8.597191,8.594620,8.591673,8.600966,8.598019,8.595448,8.592691,
                  8.599735,8.596979,8.594409,8.591463,8.600753,8.597807,8.595237,8.592480,8.599525,8.596771,
                  8.594202,8.591258,8.600542,8.597598,8.595029,8.592274,8.599317,8.596565,8.593999,8.591057,
                  8.600333,8.597391,8.594825,8.592073,8.599110,8.596361,8.593797,8.590859,8.600125,8.597186,
                  8.594623,8.591874,8.598901,8.596156,8.593596,8.590662,8.599915,8.596980,8.594420,8.591675,
                  8.598688,8.595946,8.593390,8.590460,8.599700,8.596769,8.594213,8.591472,8.598470,8.595732,
                  8.593180,8.590253,8.599480,8.596554,8.594001,8.591264,8.598247,8.595513,8.592964,8.590042,
                  8.599257,8.596334,8.593785,8.591051,8.598021,8.595290,8.592745,8.589826,8.599028,8.596110,
                  8.593564,8.590834,8.597790,8.595063,8.592521,8.589606,8.598797,8.595882,8.593339,8.590612,
                  8.597556,8.594832,8.592293,8.589381,8.598561,8.595650,8.593110,8.590387,8.597318,8.594598,
                  8.592061,8.589153,8.598322,8.595414,8.592878,8.590157,8.597077,8.594359,8.591826,8.588921,
                  8.598080,8.595175,8.592641,8.589924,8.596833,8.594118,8.591587,8.588685,8.597835,8.594933,
                  8.592402,8.589687,8.596587,8.593874,8.591345,8.588445,8.597588,8.594688,8.592159,8.589446,
                  8.596337,8.593626,8.591099,8.588201,8.597337,8.594440,8.591912,8.589201,8.596084,8.593375,
                  8.590848,8.587952,8.597084,8.594188,8.591662,8.588952,8.595829,8.593120,8.590595,8.587699,
                  8.596829,8.593933,8.591408,8.588699,8.595572,8.592863,8.590338,8.587442,8.596571,8.593676,
                  8.591151,8.588442,8.595312,8.592604,8.590078,8.587182,8.596312,8.593417,8.590891,8.588182,
                  8.595052,8.592342,8.589816,8.586919,8.596052,8.593156,8.590629,8.587920,8.594790,8.592079,
                  8.589552,8.586654,8.595791,8.592893,8.590365,8.587655,8.594528,8.591815,8.589286,8.586386,
                  8.595529,8.592630,8.590100,8.587388,8.594265,8.591550,8.589019,8.586117,8.595267,8.592365,
                  8.589834,8.587119,8.594003,8.591285,8.588752,8.585847,8.595006,8.592101,8.589567,8.586850,
                  8.593742,8.591022,8.588485,8.585577,8.594746,8.591838,8.589302,8.586582,8.593484,8.590762,
                  8.588223,8.585312,8.594489,8.591579,8.589040,8.586317,8.593230,8.590505,8.587965,8.585052,
                  8.594236,8.591323,8.588783,8.586058,8.592979,8.590252,8.587710,8.584795,8.593985,8.591071,
                  8.588528,8.585802,8.592729,8.590002,8.587458,8.584542,8.593736,8.590820,8.588277,8.585549,
                  8.592482,8.589753,8.587209,8.584292,8.593489,8.590572,8.588028,8.585300,8.592235,8.589507,
                  8.586962,8.584045,8.593242,8.590326,8.587781,8.585053,8.591989,8.589261,8.586717,8.583801,
                  8.592996,8.590080,8.587536,8.584808,8.591743,8.589016,8.586473,8.583558,8.592750,8.589835,
                  8.587292,8.584565,8.591497,8.588772,8.586230,8.583317,8.592503,8.589590,8.587048,8.584323)
```

```{r}
PLANE_HEIGHT_VARIATION<-c(65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,68,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,67,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,66,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,65,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,64,63,63,63,63,63,63,63,63,62,62,62,62,62,62,62,62,62,62,62,62,62,62,62,62,61,61,61,61,61,61,61,61,60,60,60,60,60,60,60,60,59,59,59,59,59,59,59,59,58,58,58,58,58,58,58,58,57,57,57,57,57,57,57,57,56,56,56,56,56,56,56,56,55,55,55,55,55,55,55,55,53,53,53,53,53,53,53,53,52,52,52,52,52,52,52,52,51,51,51,51,51,51,51,51,50,50,50,50,50,50,50,50,49,49,49,49,49,49,49,49,47,47,47,47,47,47,47,47,46,46,46,46,46,46,46,46,46,46,46,46,46,46,46,46,45,45,45,45,45,45,45,45,44,44,44,44,44,44,44,44,44,44,44,44,44,44,44,44,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,42,42,42,42,42,42,42,42,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,40,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,41,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,42,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43,43)
```

```{r}
BasisDaten_test<-data.frame(
  POSITIONS=NA,
  POSITION_ID=seq(1:1000),
  POSITION_ID_CONTROLLED=1,
  Dataset_ID=NA,
  TRIP_ID=1,
  CRUISENO='AreaA_Summer_2025',
  CAMERA_NUMBER=c(1, 2, 3, 4, 5, 6, 7, 8),
  TRANSECT_NUMBER=rep(1:8, each=(1000/8)),
  DATE='20250616',
  TIME='09:00:00',
  LAT_PIC_CENTER=LAT_PIC_CENTER,
  LON_PIC_CENTER=LON_PIC_CENTER,
  PLANE_FLIGHT_HEIGHT=500,
  PIC_AREA_ANALYSED=round(runif(1000,0,0.05),2),
  GLARE=floor(runif(1000, min=0, max=3)),
  SEASTATE=floor(runif(1000, min=0, max=3)),
  TURBIDITY=floor(runif(1000, min=1, max=3)),
  ICE=0,
  CLARITY=floor(runif(1000, min=0, max=3)),
  PIC_QUALITY=1,
  PIC_FILE_NAME=NA,
  NOTES=NA
  )
BasisDaten_test
```


```{r}
BasisDaten_test<-BasisDaten_test %>%
  mutate(PIC_FILE_NAME=paste0("CAM",
                              CAMERA_NUMBER,"-",
                              rep(1:4, times=250),
                              rep(c("L","L","L","L","R","R","R","R"),times=125)))
```

```{r}
BasisDaten_test$POSITION_ID_CONTROLLED[floor(runif(744, min=0, max=1000))]<-NA
BasisDaten_test$POSITION_ID_CONTROLLED[floor(runif(6, min=0, max=1000))]<-2
BasisDaten_test$POSITION_ID_CONTROLLED[floor(runif(3, min=0, max=1000))]<-3
```

```{r}
BasisDaten_test %>%
  group_by(POSITION_ID_CONTROLLED)%>%
  tally()
```

```{r}
BasisDaten_test %>%
  rename(`POSITION ID_CONTROLLED`=POSITION_ID_CONTROLLED)
```


```{r}
BasisDaten_test<-BasisDaten_test %>%
  mutate(PLANE_FLIGHT_HEIGHT=500+PLANE_HEIGHT_VARIATION)
```










# End of document
